### 2018-11-26 paper.tex
Start on paper

\documentclass[letterpaper]{article}

\usepackage{natbib,alifeconf}  %% The order is important
\usepackage{url}

% *****************
%  Requirements:
% *****************
%
% - All pages sized consistently at 8.5 x 11 inches (US letter size).
% - PDF length <= 8 pages for full papers, <=2 pages for extended
%    abstracts.
% - Abstract length <= 250 words.
% - No visible crop marks.
% - Images at no greater than 300 dpi, scaled at 100%.
% - Embedded open type fonts only.
% - All layers flattened.
% - No attachments.
% - All desired links active in the files.

% Note that the PDF file must not exceed 5 MB if it is to be indexed
% by Google Scholar. Additional information about Google Scholar
% can be found here:
% http://www.google.com/intl/en/scholar/inclusion.html.

% If your system does not generate letter format documents by default,
% you can use the following workflow:
% latex example
% bibtex example
% latex example ; latex example
% dvips -o example.ps -t letterSize example.dvi
% ps2pdf example.ps example.pdf

% For pdflatex users:
% The alifeconf style file loads the "graphicx" package, and
% this may lead some users of pdflatex to experience problems.
% These can be fixed by editing the alifeconf.sty file to specify:
% \usepackage[pdftex]{graphicx}
%   instead of
% \usepackage{graphicx}.
% The PDF output generated by pdflatex should match the required
% specifications and obviously the dvips and ps2pdf steps become
% unnecessary.

% Note:  Some laser printers have a serious problem printing TeX
% output. The use of ps type I fonts should avoid this problem.

\title{They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games}
\author{Joel Tibbetts and Patrick Nuckolls\\
\mbox{}\\
Grinnell College, Grinnell, IA 50112 \\
} % email of corresponding author

% For several authors from the same institution use the same number to
% refer to one address.
%
% If the names do not fit well on one line use
%         Author 1, Author 2 ... \\ {\Large\bf Author n} ...\\ ...
%
% If the title and author information do not fit in the area
% allocated, place \setlength\titlebox{<new height>} after the
% \documentclass line where <new height> is 2.25in

\def\tavs{\textit{They are Very Smart}}
\begin{document}
\maketitle

\begin{abstract}
 \tavs~is a destructible tower defense game that explores the viability of short term evolution of neural nets for pathfinding in an adapting adversarial environment. 
\end{abstract}

\section{Introduction}
\tavs~is a real-time tower defense game with evolving enemies; which is to say that the player places down towers and other defenses in real time to fend off waves of enemies attempting to destroy the player's "home base." In typical tower defense games, after killing one group of enemies, another comes which is usually stronger than the previous, due to a pre-ordained set of constraints. \textit{They are Very Smart} differs from typical tower defense games in that enemy progression is not determined by divine force (i.e., the game developer), but rather evolves as a result of a genetic algorithm which controls the enemies' damage, movement speed, health, and navigation.

\begin{itemize}
    \item Description of tower-defense UI
    \item Placement of walls vs. towers
    \item "Spawn points" for zombies
    \item Central defensible location
    \item Economy
    \item Game end/lack thereof
\end{itemize}

\tavs was initially inspired by Numantian Games' \textit{They Are Billions}, a game in which a player must build defenses in order to fend off a zombie apocalypse. The game features massive numbers of zombies. This project emerged from an interest in what \textit{They Are Billions} would be like if the zombies could actually think for themselves. The result is significantly pared down in comparison, as the focus has been on zombie evolution as opposed to player interactivity and enjoyability. However, similiarities to \textit{They Are Billions} can be seen in the resource management system, the player's defense of a citadel, and need to fend off the faceless hordes. \textit{They Are Billions} puts additional emphasis on world generation, player exploration, and narrative elements.

Insert picture of \textit{They Are Billions} gameplay here.

\section{Background}
In \tavs, we utilize a basic genetic algorithm to train a recurrent neural network generated using the Neuroevolution of Augmenting Topologies (NEAT) method, ~cite http://sharpneat.sourceforge.net/~ with https://www.heatonresearch.com/encog/, which is a generalized deep-learning library that includes implementations of NEAT and HyperNEAT.

NEAT is particularly applicable to our issue because it allows the evolution of different topologies and weights in neural networks at the same time, unlike standard back-propagation learning, and is also well-suited for encoding into a genome for evolution. NEAT works essentially by encoding a function that then generates a neural net (citation needed), starting out with low complexity of topology, which can then evolve towards more complex topologies.

Insert helpful diagram here

\section{Tutorial}
Overview
\begin{itemize}
    \item Unity
    \item Tower Defense tutorial
    \item Action Game Framework
    \item Creating custom towers
    \item Custom scripts
        \begin{itemize}
            \item Genome
            \item ZombieAgent
            \item GenomeManager
            \item ZombieAttacker
        \end{itemize}
    \item Problems importing packages
    \item Relevant parts of Encog framework
        \begin{itemize}
            \item Manually pulling out Encog training methods for neural nets
            \item Stealing Softmax function
        \end{itemize}
    \item Point array stats system
    \item Details of genetic algorithm
        \begin{itemize}
            \item Mutation
            \item Keeping track of fitness
            \item Population management
            \item Starvation function
        \end{itemize}
\end{itemize}

\section{Preliminary Results and Discussion}
Over the course of this project, we learned more about game design than we did evolutionary algorithms and artificial life. The majority of our time working on this project was spent dealing with learning the basics of Unity and C\#, which presented a very significant challenge that we vastly underestimated.

At this time, we are currently waiting on actual results from our project, but we hope that given a large enough population of zombies, we might see populations of zombies evolving to counteract players' strategies, although we may also see players coming up with ways to counteract the zombies by exploiting elements of the fitness function and construction system in ways unforeseen, possibly by playing in such a way as to allow the zombies to optimize for something other than killing the player's home base. Another possibility we might expect to see is the development of swarm or anti-swarm behavior based on the effectiveness of player defenses, as well as zombies possibly hitting minima or maxima depending on hard-coded numbers in the game environment.

In the future, we would experiment with elements such as variable damage output from towers and other defenses (so as to avoid the aforementioned numeric minima and maxima), as well as coming up with ways to encourage attacking the player's base more as time goes on.

Ultimately, we think that although evolution was the appropriate mechanism to to solve the issue at hand, game development was not the appropriate environment for this topic, given the time investment.

\section{Conclusion}
\begin{itemize}
    \item Synopsis of project
    \item Future work and next steps
\end{itemize}

\section{Acknowledgements}
\begin{itemize}
    \item Use of multiple tutorials/repositories
    \begin{itemize}
        \item Encog Machine Learning Framework
        \item Unity Tower Defense Tutorial
        \item Unity Action Game Shooter Tutorial
        \item Redzen repository for normal random numbers
        \item 
    \end{itemize}
\end{itemize}

\footnotesize
\bibliographystyle{apalike}
\bibliography{bibliography} % replace by the name of your .bib file

\end{document}

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/ArrayUtils.cs
Removed Submodules

@@ -1,0 +1,91 @@
+﻿using System;
+using System.Collections.Generic;
+
+namespace Redzen
+{
+    /// <summary>
+    /// Array static utility methods.
+    /// </summary>
+    public static class ArrayUtils
+    {
+        #region Public Static Methods
+
+        /// <summary>
+        /// Returns true if the two arrays are equal.
+        /// </summary>
+        /// <param name="x">First array.</param>
+        /// <param name="y">Second array.</param>
+        public static bool Equals<T>(T[] x, T[] y)
+        {
+            // x and y are equal if they are the same reference, or both are null.
+            if(x == y) {
+                return true;
+            }
+
+            // Test if one is null and the other not null.
+            // Note. We already tested for both being null (above).
+            if(null == x || null == y) {
+                return false;
+            }
+
+            if(x.Length != y.Length) {
+                return false;
+            }
+
+            var comp = Comparer<T>.Default;
+
+            for(int i=0; i < x.Length; i++)
+            {
+                if(comp.Compare(x[i], y[i]) != 0){
+                    return false;
+                }
+            }
+            return true;
+        }
+
+        /// <summary>
+        /// Returns true if all of the array elements are equal to the given value.
+        /// </summary>
+        /// <param name="arr">Array to test..</param>
+        /// <param name="v">The test value.</param>
+        public static bool Equals<T>(T[] arr, T v)
+        {
+            var comp = Comparer<T>.Default;
+
+            for(int i=0; i < arr.Length; i++)
+            {
+                if(comp.Compare(arr[i], v) != 0){
+                    return false;
+                }
+            }
+            return true;
+        }
+
+        // TODO: Create overload based on Span<T> once it is available.
+        /// <summary>
+        /// Returns true if the elements of the specified array sub-segment are equal to the given value.
+        /// </summary>
+        /// <param name="arr">Array to test..</param>
+        /// <param name="v">The test value.</param>
+        public static bool Equals<T>(
+            T[] arr, T v,
+            int offset, int length)
+        {
+            if(offset < 0 || length < 0 || offset + length > arr.Length) {
+                throw new ArgumentOutOfRangeException();
+            }
+
+            var comp = Comparer<T>.Default;
+
+            for(int i=offset; i < offset + length; i++)
+            {
+                if(comp.Compare(arr[i], v) != 0){
+                    return false;
+                }
+            }
+            return true;
+        }
+
+        #endregion
+    }
+}

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Collections/IntStack.cs

@@ -1,0 +1,172 @@
+﻿using System;
+using System.Diagnostics;
+
+namespace Redzen.Collections
+{
+    /// <summary>
+    /// A stack of int32 values.
+    /// A simpler alternative to Stack<int> that provides additional Poke() and TryPoke() methods.
+    /// </summary>
+    public sealed class IntStack
+    {
+        #region Fields
+
+        const int __defaultCapacity = 4;
+        int[] _array; 
+        int _size; 
+        
+        #endregion
+
+        #region Constructors
+
+        /// <summary>
+        /// Default constructor.
+        /// </summary>
+        public IntStack()
+        {
+            _array = new int[__defaultCapacity];
+        }
+
+        /// <summary>
+        /// Construct with the given initial capacity.
+        /// </summary>
+        /// <param name="capacity">Initial capacity.</param>
+        public IntStack(int capacity)
+        {
+            if (capacity < 0) {
+                throw new ArgumentOutOfRangeException("Capacity must be non-negative.");
+            }
+            _array = new int[capacity];
+        }
+
+        #endregion
+
+        #region Properties
+
+        /// <summary>
+        /// Gets the number of items on the stack.
+        /// </summary>
+        public int Count => _size;
+
+        #endregion
+
+        #region Public Methods
+
+        /// <summary>
+        /// Pushes a value onto the top of the stack.
+        /// </summary>
+        /// <param name="val">The value to push.</param>
+        public void Push(int val)
+        {
+            if (_size == _array.Length) {
+                Array.Resize(ref _array, (_array.Length == 0) ? __defaultCapacity : 2 * _array.Length);
+            }
+            _array[_size++] = val;
+        }
+
+        /// <summary>
+        /// Pop a value from the top of the stack.
+        /// </summary>
+        /// <returns>The popped value from the top of the stack.</returns>
+        public int Pop()
+        {
+            if(0 == _size) {
+                ThrowForEmptyStack();
+            }
+            
+            return _array[--_size];
+        }
+
+        /// <summary>
+        /// Attempt to pop a value from the top of the stack.
+        /// </summary>
+        /// <param name="result">The value from the top of the stack.</param>
+        /// <returns>True if successful, otherwise false.</returns>
+        public bool TryPop(out int result)
+        {
+            if(0 == _size)
+            {
+                result = default(int);
+                return false;
+            }
+
+            result = _array[--_size];
+            return true;
+        }
+
+        /// <summary>
+        /// Returns the value at the top of the stack without popping it.
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Collections/LightweightStack.cs

@@ -1,0 +1,172 @@
+﻿using System;
+using System.Diagnostics;
+
+namespace Redzen.Collections
+{
+    /// <summary>
+    /// A lightweight generic stack.
+    /// A simpler alternative to Stack<int> that provides additional Poke() and TryPoke() methods.
+    /// </summary>
+    public sealed class LightweightStack<T>
+    {
+        #region Fields
+
+        const int __defaultCapacity = 4;
+        T[] _array; 
+        int _size; 
+        
+        #endregion
+
+        #region Constructors
+
+        /// <summary>
+        /// Default constructor.
+        /// </summary>
+        public LightweightStack()
+        {
+            _array = new T[__defaultCapacity];
+        }
+
+        /// <summary>
+        /// Construct with the given initial capacity.
+        /// </summary>
+        /// <param name="capacity">Initial capacity.</param>
+        public LightweightStack(int capacity)
+        {
+            if (capacity < 0) {
+                throw new ArgumentOutOfRangeException("Capacity must be non-negative.");
+            }
+            _array = new T[capacity];
+        }
+
+        #endregion
+
+        #region Properties
+
+        /// <summary>
+        /// Gets the number of items on the stack.
+        /// </summary>
+        public int Count { get { return _size; } }
+
+        #endregion
+
+        #region Public Methods
+
+        /// <summary>
+        /// Pushes a value onto the top of the stack.
+        /// </summary>
+        /// <param name="val">The value to push.</param>
+        public void Push(T val)
+        {
+            if (_size == _array.Length) {
+                Array.Resize(ref _array, (_array.Length == 0) ? __defaultCapacity : 2 * _array.Length);
+            }
+            _array[_size++] = val;
+        }
+
+        /// <summary>
+        /// Pop a value from the top of the stack.
+        /// </summary>
+        /// <returns>The popped value from the top of the stack.</returns>
+        public T Pop()
+        {
+            if(0 == _size) {
+                ThrowForEmptyStack();
+            }
+            
+            return _array[--_size];
+        }
+
+        /// <summary>
+        /// Attempt to pop a value from the top of the stack.
+        /// </summary>
+        /// <param name="result">The value from the top of the stack.</param>
+        /// <returns>True if successful, otherwise false.</returns>
+        public bool TryPop(out T result)
+        {
+            if(0 == _size)
+            {
+                result = default(T);
+                return false;
+            }
+
+            result = _array[--_size];
+            return true;
+        }
+
+        /// <summary>
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Linq/EnumerableUtils.cs

@@ -1,0 +1,51 @@
+﻿using System;
+using System.Collections.Generic;
+using Redzen.Random;
+
+namespace Redzen.Linq
+{
+    /// <summary>
+    /// Utility methods related to LINQ and IEnumerable.
+    /// </summary>
+    public class EnumerableUtils
+    {
+        /// <summary>Generates a sequence of integral numbers within a specified range and in random order.</summary>
+        /// <param name="start">The value of the first integer in the sequence.</param>
+        /// <param name="count">The number of sequential integers to generate.</param>
+        /// <returns>A new IEnumerable{int}.</returns>
+        public static IEnumerable<int> RangeRandomOrder(int start, int count, IRandomSource rng)
+        {
+	        if (count < 0 || (((long)start + count) - 1L) > int.MaxValue) {    
+		        throw new ArgumentOutOfRangeException("count");
+	        }
+
+            // Create an array of all indexes to be yielded.
+            int[] arr = new int[count];
+            for(int i=0; i < count; i++) {
+                arr[i] = start + i;
+            }
+
+            // Yield all values in turn, applying a Fisher–Yates shuffle as we go in order to randomize the yield order.
+            // See https://en.wikipedia.org/wiki/Fisher%E2%80%93Yates_shuffle
+	        for (int i=count-1; i > 0; i--)
+	        {
+                // Select at random from the remaining available slots.
+                int selectIdx = rng.Next(i + 1);
+
+                // Store the yield value.
+                int tmp = arr[selectIdx];
+
+                // Replace the selected slot value with a value that has not yet been selected.
+                // This is half of the Fisher–Yates swap, but since we don't need the final 
+                // shuffled array we can omit moving the yielded value into its new slot.
+                arr[selectIdx] = arr[i];
+
+                // Yield the value from the randomly selected slot.
+		        yield return tmp;
+	        }
+
+            // Yield final value.
+            yield return arr[0];	        
+        }
+    }
+}

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/MathUtils.cs

@@ -1,0 +1,223 @@
+﻿using System;
+
+namespace Redzen
+{
+    public static class MathUtils
+    {
+        #region Static Fields
+
+        static readonly int[] __log2_32 = new int[32]
+        {
+            0,   9,  1, 10, 13, 21, 2, 29,
+            11, 14, 16, 18, 22, 25, 3, 30,
+            8,  12, 20, 28, 15, 17, 24, 7,
+            19, 27, 23,  6, 26,  5,  4, 31
+        };
+
+        static readonly int[] __log2_64 = new int[64]
+        {
+            63,  0, 58,  1, 59, 47, 53,  2,
+            60, 39, 48, 27, 54, 33, 42,  3,
+            61, 51, 37, 40, 49, 18, 28, 20,
+            55, 30, 34, 11, 43, 14, 22,  4,
+            62, 57, 46, 52, 38, 26, 32, 41,
+            50, 36, 17, 19, 29, 10, 13, 21,
+            56, 45, 25, 31, 35, 16,  9, 12,
+            44, 24, 15,  8, 23,  7,  6,  5
+        };
+
+        #endregion
+
+        #region Public Static Methods
+
+        /// <summary>
+        /// Returns true if the input value is an integer power of two.
+        /// </summary>
+        /// <param name="x">The value to test.</param>
+        /// <returns>True if the input value is an integer power of two; otherwise false.</returns>
+        public static bool IsPowerOfTwo(int x)
+        {
+            // From: https://stackoverflow.com/questions/600293/how-to-check-if-a-number-is-a-power-of-2
+            return (x != 0) && (x & (x - 1)) == 0;
+        }
+
+        /// <summary>
+        /// Returns true if the input value is an integer power of two.
+        /// </summary>
+        /// <param name="x">The value to test.</param>
+        /// <returns>True if the input value is an integer power of two; otherwise false.</returns>
+        public static bool IsPowerOfTwo(long x)
+        {
+            // From: https://stackoverflow.com/questions/600293/how-to-check-if-a-number-is-a-power-of-2
+            return (x != 0) && (x & (x - 1)) == 0;
+        }
+
+        /// <summary>
+        /// Calculates two to the power of the given integer exponent.
+        /// </summary>
+        /// <param name="exponent">The integer exponent (0 &lt;= exponent &lt; 31)</param>
+        public static int PowerOfTwo(int exponent)
+        {
+            if (exponent < 0 || exponent > 30) {
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Numerics/Distributions/Double/ZigguratGaussian.cs

@@ -1,0 +1,456 @@
+﻿using System;
+using System.Diagnostics;
+using Redzen.Random;
+
+namespace Redzen.Numerics.Distributions.Double
+{
+    // ENHANCEMENT: Further performance improvement can be obtained by using a less precise method
+    // whereby we represent the distribution curve as a piecewise linear curve, i.e. approximate
+    // the curve using stacked trapezoids instead of stacked rectangles, and skip handling of the
+    // corner cases where we would normally perform expensive calculations to obtain precise 
+    // results. Such an approach should be suitable for generating mutations for evolutionary
+    // computing.
+    // For details about this approach see:
+    // Hardware-Optimized Ziggurat Algorithm for High-Speed Gaussian Random Number Generators,
+    // Hassan M. Edrees, Brian Cheung, McCullen Sandora, David Nummey, Deian Stefan
+    // (http://www.ee.cooper.edu/~stefan/pubs/conference/ersa2009.pdf)
+    //
+    /// <summary>
+    /// Static methods for taking samples from Gaussian distributions using the Ziggurat algorithm.
+    /// </summary>
+    /// <remarks>
+    /// A fast Gaussian distribution sampler for .NET
+    /// Colin Green, 2011-09-11
+    ///
+    /// An implementation of the Ziggurat algorithm for random sampling from a Gaussian 
+    /// distribution. See:
+    ///  - Wikipedia:Ziggurat algorithm (http://en.wikipedia.org/wiki/Ziggurat_algorithm).
+    ///  - The Ziggurat Method for Generating Random Variables, George Marsaglia and
+    ///    Wai Wan Tsang (http://www.jstatsoft.org/v05/i08/paper).
+    ///  - An Improved Ziggurat Method to Generate Normal Random Samples, Jurgen A Doornik 
+    ///    (http://www.doornik.com/research/ziggurat.pdf)
+    ///  
+    /// 
+    /// Ziggurat Algorithm Overview
+    /// ============================
+    /// 
+    /// Consider the right hand side of the Gaussian probability density function (for x >=0) as
+    /// described by y = f(x). This half of the distribution is covered by a series of stacked
+    /// horizontal rectangles, like so:
+    /// 
+    ///  _____
+    /// |     |                    R6  S6
+    /// |     |
+    /// |_____|_                   
+    /// |       |                  R5  S5
+    /// |_______|_                 
+    /// |         |                R4  S4
+    /// |_________|__       
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Numerics/HistogramData.cs

@@ -1,0 +1,99 @@
+﻿/* ***************************************************************************
+ * This file is part of the Redzen code library.
+ * 
+ * Copyright 2015-2017 Colin Green (colin.green1@gmail.com)
+ *
+ * Redzen is free software; you can redistribute it and/or modify
+ * it under the terms of The MIT License (MIT).
+ *
+ * You should have received a copy of the MIT License
+ * along with Redzen; if not, see https://opensource.org/licenses/MIT.
+ */
+
+using System;
+
+namespace Redzen.Numerics
+{
+    // TODO: Check if there is an equivalent class in MathNet.Numerics.
+    /// <summary>
+    /// Histogram data. Frequency counts arranged into bins..
+    /// </summary>
+    public sealed class HistogramData
+    {
+        double _min;
+        double _max;
+        double _incr;
+        int[] _frequencyArr;
+
+        #region Constructor
+
+        /// <summary>
+        /// Construct with the provided frequency distribution data.
+        /// </summary>
+        /// <param name="min">The minimum value in the data series the distribution represents.</param>
+        /// <param name="max">The maximum value in the data series the distribution represents.</param>
+        /// <param name="increment">The range of a single category bucket.</param>
+        /// <param name="frequencyArr">The array of category frequency counts.</param>
+        public HistogramData(double min, double max, double increment, int[] frequencyArr)
+        {
+            _min = min;
+            _max = max;
+            _incr = increment;
+            _frequencyArr = frequencyArr;
+        }
+
+        #endregion
+
+        #region Properties
+
+        /// <summary>
+        /// The minimum value in the data series the distribution represents.
+        /// </summary>
+        public double Min
+        {
+            get { return _min; }
+        }
+
+        /// <summary>
+        /// The maximum value in the data series the distribution represents.
+        /// </summary>
+        public double Max
+        {
+            get { return _max; }
+        }
+
+        /// <summary>
+        /// The range of a single category bucket.
+        /// </summary>
+        public double Increment
+        {
+            get { return _incr; }
+        }
+
+        /// <summary>
+        /// The array of category frequency counts.
+        /// </summary>
+        public int[] FrequencyArray
+        {
+            get { return _frequencyArr; }
+        }
+
+        #endregion
+
+        #region Public Methods
+
+        /// <summary>
+        /// Gets the index of the bucket that covers the specified x value. Throws an exception if x is 
+        /// outside the range of represented by the distribution buckets.
+        /// </summary>
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Numerics/NumericsUtils.cs

@@ -1,0 +1,109 @@
+﻿/* ***************************************************************************
+ * This file is part of the Redzen code library.
+ * 
+ * Copyright 2015-2017 Colin Green (colin.green1@gmail.com)
+ *
+ * Redzen is free software; you can redistribute it and/or modify
+ * it under the terms of The MIT License (MIT).
+ *
+ * You should have received a copy of the MIT License
+ * along with Redzen; if not, see https://opensource.org/licenses/MIT.
+ */
+
+using System;
+using System.Collections.Generic;
+//using System.Diagnostics;
+using Redzen.Random;
+//using Redzen.Sorting;
+
+namespace Redzen.Numerics
+{
+    /// <summary>
+    /// General purpose numeric helper methods.
+    /// </summary>
+    public static class NumericsUtils
+    {
+        /// <summary>
+        /// Rounds up or down to a whole number by using the fractional part of the input value
+        /// as the probability that the value will be rounded up.
+        /// 
+        /// This is useful if we wish to round values and then sum them without generating a rounding bias.
+        /// For monetary rounding this problem is solved with rounding to e.g. the nearest even number which
+        /// then causes a bias towards even numbers.
+        /// 
+        /// This solution is more appropriate for certain types of scientific values.
+        /// </summary>
+        public static double ProbabilisticRound(double val, IRandomSource rng)
+        {
+            double integerPart = Math.Floor(val);
+            double fractionalPart = val - integerPart;
+            return rng.NextDouble() < fractionalPart ? integerPart + 1.0 : integerPart;
+        }
+
+        /// <summary>
+        /// Calculates the median value in a list of sorted values.
+        /// </summary>
+        public static double CalculateMedian(IList<double> valueList)
+        {
+            //Debug.Assert(valueList.Count != 0 && SortUtils.IsSortedAscending(valueList), "CalculateMedian() requires non-zero length sorted list of values.");
+
+            if(1 == valueList.Count) {
+                return valueList[0];
+            }
+
+            if(valueList.Count % 2 == 0)
+            {   // Even number of values. The values are already sorted so we simply take the
+                // mean of the two central values.
+                int idx = valueList.Count / 2;
+                return (valueList[idx - 1] + valueList[idx]) / 2.0;
+            }
+
+            // Odd number of values. Return the middle value.
+            // (Note. integer division truncates fractional part of result).
+            return valueList[valueList.Count / 2];
+        }
+
+        /// <summary>
+        /// Calculate a frequency distribution for the provided array of values.
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Random/DefaultRandomSeedSource.cs

@@ -1,0 +1,138 @@
+﻿using System;
+using System.Security.Cryptography;
+using System.Threading;
+
+namespace Redzen.Random
+{
+    /// <summary>
+    /// Default implementation of IRandomSeedSource.
+    /// A source of seed values for use by pseudo-random number generators (PRNGs).
+    /// </summary>
+    /// <remarks>
+    /// This implementation uses multiple seed PRNGs initialised with high quality crypto random seed state. 
+    /// 
+    /// New seeds are generated by rotating through the seed PRNGs to generate seed values. Using multiple seed PRNGs
+    /// in this way (A) increases the state space that is being sampled from, (B) improves thread concurrency by 
+    /// allowing each PRNG to be in use concurrently, and (C) greatly improves performance compared to using
+    /// a crypto random source for all PRNGs. I.e. this class is a compromise between using perfectly random 
+    /// (crypto) seed data, versus using pseudo-random data but with increased performance.
+    /// </remarks>
+    public class DefaultRandomSeedSource : IRandomSeedSource
+    {
+        #region Instance Fields
+
+        readonly uint _concurrencyLevel;
+        readonly Xoshiro256StarStarRandom[] _seedRngArr;
+        readonly SemaphoreSlim _semaphore;
+        // Round robin accumulator.
+        int _roundRobinAcc = 0;
+
+        #endregion
+
+        #region Constructors
+
+        /// <summary>
+        /// Construct with the default concurrency level.
+        /// </summary>
+        public DefaultRandomSeedSource()
+            : this(Environment.ProcessorCount)
+        {}
+
+        /// <summary>
+        /// Construct with the specified minimum concurrency level.
+        /// </summary>
+        /// <remarks>
+        /// minConcurrencyLevel must be at least one, an exception is thrown if it is less than 1 (i.e. zero or negative).
+        /// The actual concurrency level is required to be a power of two, thus the actual level is chosen to be the 
+        /// nearest power of two that is greater than or equal to minConcurrencyLevel/
+        /// </remarks>
+        public DefaultRandomSeedSource(int minConcurrencyLevel)
+        {
+            if(minConcurrencyLevel < 1) {
+                throw new ArgumentException("Must be at least 1.", nameof(minConcurrencyLevel));
+            }
+
+            // The actual concurrency level is required to be a power of two, thus the actual level is chosen
+            // to be the nearest power of two that is greater than or equal to minConcurrencyLevel.
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Random/IRandomSource.cs

@@ -1,0 +1,99 @@
+﻿/* ***************************************************************************
+ * This file is part of the Redzen code library.
+ * 
+ * Copyright 2015-2017 Colin Green (colin.green1@gmail.com)
+ *
+ * Redzen is free software; you can redistribute it and/or modify
+ * it under the terms of The MIT License (MIT).
+ *
+ * You should have received a copy of the MIT License
+ * along with Redzen; if not, see https://opensource.org/licenses/MIT.
+ */
+
+namespace Redzen.Random
+{
+    /// <summary>
+    /// A source of random values.
+    /// </summary>
+    public interface IRandomSource
+    {
+        /// <summary>
+        /// Re-initialises the random number generator state using the provided seed value.
+        /// </summary>
+        void Reinitialise(ulong seed);
+
+        /// <summary>
+        /// Generates a random Int32 over the interval [0, int.MaxValue), i.e. exclusive of Int32.MaxValue.
+        /// </summary>
+        int Next();
+
+        /// <summary>
+        /// Generate a random Int32 over the interval [0 to maxValue), i.e. excluding maxValue.
+        /// </summary>
+        int Next(int maxValue);
+
+        /// <summary>
+        /// Generate a random Int32 over the interval [minValue, maxValue), i.e. excluding maxValue.
+        /// maxValue must be >= minValue. minValue may be negative.
+        /// </summary>
+        int Next(int minValue, int maxValue);
+
+        /// <summary>
+        /// Generates a random double over the interval [0, 1), i.e. inclusive of 0.0 and exclusive of 1.0.
+        /// </summary>
+        double NextDouble();
+
+        /// <summary>
+        /// Generate a random double over the interval [0, 1), i.e. inclusive of 0.0 and exclusive of 1.0.
+        /// </summary>
+        /// <remarks>
+        /// Uses an alternative sampling method that is capable of generating all possible values in the
+        /// interval [0,1) that can be represented by a double precision float. Note however that this method 
+        /// is significantly slower than NextDouble().
+        /// </remarks>
+        double NextDoubleHighRes();
+
+        /// <summary>
+        /// Fills the provided byte array with random bytes.
+        /// </summary>
+        /// <param name="buffer">The byte array to fill with random values.</param>
+        void NextBytes(byte[] buffer);
+
+        /// <summary>
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Random/RandomSourceBase.cs

@@ -1,0 +1,353 @@
+﻿using System;
+using System.Runtime.CompilerServices;
+
+namespace Redzen.Random
+{
+    public abstract class RandomSourceBase
+    {
+        // Constants.
+        const double INCR_DOUBLE = 1.0 / (1UL << 53);
+        const float INCR_FLOAT = 1f / (1U << 24);
+
+        #region Public Methods [System.Random functionally equivalent methods]
+
+        /// <summary>
+        /// Generate a random Int32 over the interval [0, Int32.MaxValue), i.e. exclusive of Int32.MaxValue.
+        /// </summary>
+        /// <remarks>
+        /// Int32.MaxValue is excluded in order to be functionally equivalent with System.Random.Next().
+        /// 
+        /// For slightly improved performance consider these alternatives:
+        /// 
+        ///  * NextInt() returns an Int32 over the interval [0 to Int32.MaxValue], i.e. inclusive of Int32.MaxValue.
+        /// 
+        ///  * NextUInt(). Cast the result to an Int32 to generate an value over the full range of an Int32,
+        ///    including negative values.
+        /// </remarks>
+        public int Next()
+        {
+            // Perform rejection sampling to handle the special case where the value int.MaxValue is generated;
+            // this value is outside the range of permitted values for this method. 
+            // Rejection sampling ensures we produce an unbiased sample.
+            ulong rtn;
+            do 
+            {
+                rtn = NextULongInner() & 0x7fffffffUL;
+            }
+            while(rtn == 0x7fffffffUL);
+
+            return (int)rtn;
+        }
+
+        /// <summary>
+        /// Generate a random Int32 over the interval [0 to maxValue), i.e. excluding maxValue.
+        /// </summary>
+        public int Next(int maxValue)
+        {
+            if (maxValue < 1) {
+                throw new ArgumentOutOfRangeException(nameof(maxValue), maxValue, "maxValue must be > 0");
+            }
+
+            if(1 == maxValue) {
+                return 0;
+            }
+
+            return NextInner(maxValue);
+        }
+
+        /// <summary>
+        /// Generate a random Int32 over the interval [minValue, maxValue), i.e. excluding maxValue.
+        /// maxValue must be >= minValue. minValue may be negative.
+        /// </summary>
+        public int Next(int minValue, int maxValue)
+        {
+            if (minValue >= maxValue) {
+                throw new ArgumentOutOfRangeException(nameof(maxValue), maxValue, "maxValue must be > minValue");
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Random/XorShiftRandom.cs

@@ -1,0 +1,527 @@
+/* ***************************************************************************
+ * This file is part of the Redzen code library.
+ * 
+ * Copyright 2005-2018 Colin Green (colin.green1@gmail.com)
+ *
+ * Redzen is free software; you can redistribute it and/or modify
+ * it under the terms of The MIT License (MIT).
+ *
+ * You should have received a copy of the MIT License
+ * along with Redzen; if not, see https://opensource.org/licenses/MIT.
+ */
+
+using System;
+using System.Runtime.CompilerServices;
+
+namespace Redzen.Random
+{
+    /// <summary>
+    /// A fast random number generator for .NET
+    /// Colin Green, January 2005
+    /// 
+    /// 
+    /// Key points:
+    ///  1) Based on a simple and fast xor-shift pseudo random number generator (RNG) specified in: 
+    ///  Marsaglia, George. (2003). Xorshift RNGs.
+    ///  http://www.jstatsoft.org/v08/i14/paper
+    ///  
+    ///  This particular implementation of xorshift has a period of 2^128-1. See the above paper to see
+    ///  how this can be easily extended if you need a longer period. At the time of writing I could find no 
+    ///  information on the period of System.Random for comparison.
+    /// 
+    ///  2) Faster than System.Random. Up to 8x faster, depending on which methods are called.
+    /// 
+    ///  3) Direct replacement for System.Random. This class implements all of the methods that System.Random 
+    ///  does plus some additional methods. The like named methods are functionally equivalent.
+    ///  
+    ///  4) Allows fast re-initialisation with a seed, unlike System.Random which accepts a seed at construction
+    ///  time which then executes a relatively expensive initialisation routine. This provides a significant speed
+    ///  improvement if you need to reset the pseudo-random number sequence many times, e.g. if you want to 
+    ///  re-generate the same sequence of random numbers many times. An alternative might be to cache random numbers 
+    ///  in an array, but that approach is limited by memory capacity and the fact that you may also want a large 
+    ///  number of different sequences cached. Each sequence can be represented by a single seed value (int) when 
+    ///  using this class.
+    /// </summary>
+    [Obsolete("Superseded by Xoshiro256StarStar (comparable performance, but passes more statistical tests and has a longer period)")]
+    public sealed class XorShiftRandom : IRandomSource
+    {
+        // Constants.
+        const double INCR_DOUBLE = 1.0 / (1UL << 32);
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Random/XorShiftRandomBuilder.cs

@@ -1,0 +1,53 @@
+﻿
+namespace Redzen.Random
+{
+    /// <summary>
+    /// A builder of XorShiftRandom instances.
+    /// </summary>
+    public class XorShiftRandomBuilder : IRandomSourceBuilder
+    {
+        readonly IRandomSeedSource _seedSource;
+
+        #region Constructors
+
+        /// <summary>
+        /// Construct with a default seed source.
+        /// </summary>
+        public XorShiftRandomBuilder()
+        {
+            _seedSource = new DefaultRandomSeedSource();
+        }
+
+        /// <summary>
+        /// Construct with the given seed source.
+        /// </summary>
+        public XorShiftRandomBuilder(
+            IRandomSeedSource seedSource)
+        {
+            _seedSource = seedSource;
+        }
+
+        #endregion
+
+        #region Public Methods
+
+        /// <summary>
+        /// Create a new instance of XorShiftRandom.
+        /// </summary>
+        public IRandomSource Create()
+        {
+            ulong seed = _seedSource.GetSeed();
+            return new XorShiftRandom(seed);
+        }
+
+        /// <summary>
+        /// Create a new instance of XorShiftRandom with the given PRNG seed.
+        /// </summary>
+        public IRandomSource Create(ulong seed)
+        {
+            return new XorShiftRandom(seed);
+        }
+
+        #endregion
+    }
+}

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Random/Xoshiro256PlusRandom.cs

@@ -1,0 +1,206 @@
+﻿// A C# port of the xorshiro256** pseudo random number generator (PRNG).
+// Original C source code was obtained from:
+//    http://xoshiro.di.unimi.it/xoshiro256starstar.c
+//
+// See original headers below for more info.
+//
+// ===========================================================================
+//
+// Written in 2018 by David Blackman and Sebastiano Vigna (vigna@acm.org)
+//
+// To the extent possible under law, the author has dedicated all copyright
+// and related and neighboring rights to this software to the public domain
+// worldwide. This software is distributed without any warranty.
+
+// See <http://creativecommons.org/publicdomain/zero/1.0/>. */
+//
+// --------
+//
+// This is xoshiro256+ 1.0, our best and fastest generator for floating-point
+// numbers. We suggest to use its upper bits for floating-point
+// generation, as it is slightly faster than xoshiro256**. It passes all
+// tests we are aware of except for the lowest three bits, which might
+// fail linearity tests (and just those), so if low linear complexity is
+// not considered an issue (as it is usually the case) it can be used to
+// generate 64-bit outputs, too.
+//
+// We suggest to use a sign test to extract a random Boolean value, and
+// right shifts to extract subsets of bits.
+//
+// The state must be seeded so that it is not everywhere zero. If you have
+// a 64-bit seed, we suggest to seed a splitmix64 generator and use its
+// output to fill s. 
+
+using System.Runtime.CompilerServices;
+using static Redzen.BitwiseUtils;
+
+namespace Redzen.Random
+{
+    /// <summary>
+    /// Xoshiro256+ (xor, shift, rotate) pseudo random number generator (PRNG).
+    /// </summary>
+    public sealed class Xoshiro256PlusRandom : RandomSourceBase, IRandomSource
+    {
+        // RNG state.
+        ulong _s0;
+        ulong _s1;
+        ulong _s2;
+        ulong _s3;
+
+        #region Constructors
+
+        /// <summary>
+        /// Initialises a new instance with a seed from the default seed source.
+        /// </summary>
+        public Xoshiro256PlusRandom()
+        {
+            Reinitialise(RandomDefaults.GetSeed());
+        }
+
+        /// <summary>
+        /// Initialises a new instance with the provided ulong seed.
+        /// </summary>
+        public Xoshiro256PlusRandom(ulong seed)
+        {
+            Reinitialise(seed);
+        }
+
+        #endregion
+
+        #region Public Methods [Re-initialisation]
+
+        /// <summary>
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Random/Xoshiro256StarStarRandom.cs

@@ -1,0 +1,201 @@
+﻿// A C# port of the xorshiro256** pseudo random number generator (PRNG).
+// Original C source code was obtained from:
+//    http://xoshiro.di.unimi.it/xoshiro256starstar.c
+//
+// See original headers below for more info.
+//
+// ===========================================================================
+//
+// Written in 2018 by David Blackman and Sebastiano Vigna (vigna@acm.org)
+//
+// To the extent possible under law, the author has dedicated all copyright
+// and related and neighboring rights to this software to the public domain
+// worldwide. This software is distributed without any warranty.
+
+// See <http://creativecommons.org/publicdomain/zero/1.0/>. */
+//
+// --------
+//
+// This is xoshiro256** 1.0, our all-purpose, rock-solid generator. It has
+// excellent (sub-ns) speed, a state space (256 bits) that is large enough
+// for any parallel application, and it passes all tests we are aware of.
+//
+// For generating just floating-point numbers, xoshiro256+ is even faster.
+//
+// The state must be seeded so that it is not everywhere zero. If you have
+// a 64-bit seed, we suggest to seed a splitmix64 generator and use its
+// output to fill s. 
+
+using System.Runtime.CompilerServices;
+using static Redzen.BitwiseUtils;
+
+namespace Redzen.Random
+{
+    /// <summary>
+    /// Xoshiro256** (xor, shift, rotate) pseudo random number generator (PRNG).
+    /// </summary>
+    public sealed class Xoshiro256StarStarRandom : RandomSourceBase, IRandomSource
+    {
+        // RNG state.
+        ulong _s0;
+        ulong _s1;
+        ulong _s2;
+        ulong _s3;
+
+        #region Constructors
+
+        /// <summary>
+        /// Initialises a new instance with a seed from the default seed source.
+        /// </summary>
+        public Xoshiro256StarStarRandom()
+        {
+            Reinitialise(RandomDefaults.GetSeed());
+        }
+
+        /// <summary>
+        /// Initialises a new instance with the provided seed.
+        /// </summary>
+        public Xoshiro256StarStarRandom(ulong seed)
+        {
+            Reinitialise(seed);
+        }
+
+        #endregion
+
+        #region Public Methods [Re-initialisation]
+
+        /// <summary>
+        /// Re-initialises the random number generator state using the provided seed.
+        /// </summary>
+        public void Reinitialise(ulong seed)
+        {
+            // Notes.
+            // The first random sample will be very strongly correlated to the value we give to the 
[…]

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/Random/Xoshiro256StarStarRandomBuilder.cs

@@ -1,0 +1,53 @@
+﻿
+namespace Redzen.Random
+{
+    /// <summary>
+    /// A builder of Xoshiro256StarStarRandom instances.
+    /// </summary>
+    public class Xoshiro256StarStarRandomBuilder : IRandomSourceBuilder
+    {
+        readonly IRandomSeedSource _seedSource;
+
+        #region Constructors
+
+        /// <summary>
+        /// Construct with a default seed source.
+        /// </summary>
+        public Xoshiro256StarStarRandomBuilder()
+        {
+            _seedSource = new DefaultRandomSeedSource();
+        }
+
+        /// <summary>
+        /// Construct with the given seed source.
+        /// </summary>
+        public Xoshiro256StarStarRandomBuilder(
+            IRandomSeedSource seedSource)
+        {
+            _seedSource = seedSource;
+        }
+
+        #endregion
+
+        #region Public Methods
+
+        /// <summary>
+        /// Create a new instance of Xoshiro256StarStarRandom.
+        /// </summary>
+        public IRandomSource Create()
+        {
+            ulong seed = _seedSource.GetSeed();
+            return new Xoshiro256StarStarRandom(seed);
+        }
+
+        /// <summary>
+        /// Create a new instance of Xoshiro256StarStarRandom with the given PRNG seed.
+        /// </summary>
+        public IRandomSource Create(ulong seed)
+        {
+            return new Xoshiro256StarStarRandom(seed);
+        }
+
+        #endregion
+    }
+}

### 2018-12-03 TD/TowerDefense/Assets/Scripts/Util/Redzen/Redzen/SearchUtils.cs

@@ -1,0 +1,61 @@
+﻿using System;
+using System.Collections.Generic;
+
+namespace Redzen
+{
+    /// <summary>
+    /// Helper methods related to binary search.
+    /// </summary>
+    public static class SearchUtils
+    {
+        /// <summary>
+        /// Searches an entire one-dimensional sorted list for a specific item, using the provided comparison function.
+        /// </summary>
+        /// <typeparam name="T">The list item type.</typeparam>
+        /// <typeparam name="V">The type of value being searched on.</typeparam>
+        /// <param name="list">The list of items to search.</param>
+        /// <param name="value">The value being search for.</param>
+        /// <param name="compareFn">Comparison function. For comparing list items based on the return value of this function rather than the items themselves.</param>
+        /// <returns>The zero-based index of an item in the list, if item is found; otherwise, a negative number that is the bitwise complement of the index of the next 
+        /// element that is larger than item or, if there is no larger element, the bitwise complement of list.Count.</returns>
+        public static int BinarySearch<T,V>(IList<T> list, V value, Func<T,V,int> compareFn)
+        {
+            return BinarySearch(list, 0, list.Count, value, compareFn);
+        }
+
+        /// <summary>
+        /// Searches a sub-range of a one-dimensional sorted list for a specific item, using the provided comparison function.
+        /// </summary>
+        /// <typeparam name="T">The list item type.</typeparam>
+        /// <typeparam name="V">The type of value being searched on.</typeparam>
+        /// <param name="list">The list of items to search.</param>
+        /// <param name="index">The starting index of the range to search.</param>
+        /// <param name="length">The length of the range to search.</param>
+        /// <param name="value">The value being search for.</param>
+        /// <param name="compareFn">Comparison function. For comparing list items based on the return value of this function rather than the items themselves.</param>
+        /// <returns>The zero-based index of an item in the list, if item is found; otherwise, a negative number that is 
+        /// the bitwise complement of the index of the next element that is larger than item or, if there is no larger element,
+        /// the bitwise complement of list.Count.</returns>
+        public static int BinarySearch<T,V>(IList<T> list, int index, int length, V value, Func<T,V,int> compareFn)
+        {
+			int lo = index;
+			int hi = index + length - 1;
+			while (lo <= hi)
+			{
+				int mid = lo + (hi - lo >> 1);
+
[…]

### 2018-12-04 paper.tex
Paper: added a bit to the tutorial

@@
 \section{Tutorial}
+
+\subsection{Running the game}
+Our game can be found at
+\href{https://github.com/YourFin/They-Are-Very-Smart}{github.com/yourfin/They-Are-Very-Smart},
+and downloaded with a standard \texttt{git clone} command. The relevant unity
+scene is then located at
+\texttt{They-Are-Very-Smart/TD/TowerDefence/Assets/Scenes/Levels/Level0/Level0.unity}
+Double clicking on this file on any computer with unity installed will open up
+the unity editor with the context for this paper.
+
 Overview

### 2018-12-04 paper.tex
Paper: add pictures
Paper: add column width to image example
Add imfig macro
Paper: add more information to discussion, mainly problems

@@
 \usepackage{url}
+\usepackage{graphicx}
+\graphicspath{ {./pictures/} }
 
@@
 
-At this time, we are currently waiting on actual results from our project, but we hope that given a large enough population of zombies, we might see populations of zombies evolving to counteract players' strategies, although we may also see players coming up with ways to counteract the zombies by exploiting elements of the fitness function and construction system in ways unforeseen, possibly by playing in such a way as to allow the zombies to optimize for something other than killing the player's home base.
-Another possibility we might expect to see is the development of swarm or anti-swarm behavior based on the effectiveness of player defenses, as well as zombies possibly hitting minima or maxima depending on hard-coded numbers in the game environment.
+At this time, we are currently waiting on actual results from our project, but
+we hope that given a large enough population of zombies, we might see
+populations of zombies evolving to counteract players' strategies. Evolution
+will likely have little trouble tackling a trivial or consistent player
+strategy, like consistently rebuilding the same towers in the same place and
+relying heavily on a single tower type, but evolution may have trouble keeping
+up with a player that consistently changes strategy over the course of the game.
+Our system of softmaxing the genome speed, health, and damage could also
+result in progressively larger values relative to the mutation rate, making it
+hard for long-evolved values to be changed in the face of changing player
+strategies.
 
-In the future, we would experiment with elements such as variable damage output from towers and other defenses (so as to avoid the aforementioned numeric minima and maxima), as well as coming up with ways to encourage attacking the player's base more as time goes on.
+may also see players coming up with ways to counteract the zombies by exploiting
+elements of the fitness function and construction system in ways unforeseen,
+possibly by playing in such a way as to allow the zombies to optimize for
+something other than killing the player's home base. Another possibility we
+might expect to see is the development of swarm or anti-swarm behavior based on
+the effectiveness of player defenses, as well as zombies possibly hitting minima
+or maxima depending on hard-coded numbers in the game environment.
 
-Ultimately, we think that although evolution was the appropriate mechanism to to solve the issue at hand, game development was not the appropriate environment for this topic, given the time investment.
+In the future, we could experiment with elements such as variable damage output
+from towers and other defenses (so as to avoid the aforementioned numeric minima
+and maxima), as well as coming up with ways to encourage attacking the player's
+base more as time goes on; this could include ways
 

### 2018-12-04 Unity/Assets/Scripts/Camera/CameraFollow.cs
Remove old shooter tutorial code

@@ -1,22 +1,0 @@
-﻿using System.Collections;
-using System.Collections.Generic;
-using UnityEngine;
-
-public class CameraFollow : MonoBehaviour {
-
-    public Transform target;
-    public float smoothing = 5f;
-
-    Vector3 offset;
-
-    void Start()
-    {
-        offset = transform.position - target.position;    
-    }
-
-    void FixedUpdate()
-    {
-        Vector3 targetCamPos = target.position + offset;
-        transform.position = Vector3.Lerp(transform.position, targetCamPos, smoothing * Time.deltaTime);
-    }
-}

### 2018-12-04 Unity/Assets/Scripts/Enemy/EnemyHealth.cs

@@ -1,80 +1,0 @@
-﻿using UnityEngine;
-
-public class EnemyHealth : MonoBehaviour
-{
-    public int startingHealth = 100;
-    public int currentHealth;
-    public float sinkSpeed = 2.5f;
-    public int scoreValue = 10;
-    public AudioClip deathClip;
-
-
-    Animator anim;
-    AudioSource enemyAudio;
-    ParticleSystem hitParticles;
-    CapsuleCollider capsuleCollider;
-    bool isDead;
-    bool isSinking;
-
-
-    void Awake ()
-    {
-        anim = GetComponent <Animator> ();
-        enemyAudio = GetComponent <AudioSource> ();
-        hitParticles = GetComponentInChildren <ParticleSystem> ();
-        capsuleCollider = GetComponent <CapsuleCollider> ();
-
-        currentHealth = startingHealth;
-    }
-
-
-    void Update ()
-    {
-        if(isSinking)
-        {
-            transform.Translate (-Vector3.up * sinkSpeed * Time.deltaTime);
-        }
-    }
-
-
-    public void TakeDamage (int amount, Vector3 hitPoint)
-    {
-        if(isDead)
-            return;
-
-        enemyAudio.Play ();
-
-        currentHealth -= amount;
-            
-        hitParticles.transform.position = hitPoint;
-        hitParticles.Play();
-
-        if(currentHealth <= 0)
-        {
-            Death ();
-        }
-    }
-
-
-    void Death ()
-    {
-        isDead = true;
-
-        capsuleCollider.isTrigger = true;
-
-        anim.SetTrigger ("Dead");
-
-        enemyAudio.clip = deathClip;
-        enemyAudio.Play ();
-    }
-
-
-    public void StartSinking ()
-    {
-        GetComponent <UnityEngine.AI.NavMeshAgent>().enabled = false;
-        GetComponent <Rigidbody> ().isKinematic = true;
-        isSinking = true;
-        ScoreManager.score += scoreValue;
-        Destroy (gameObject, 2f);
-    }
-}

### 2018-12-04 Unity/Assets/Scripts/Enemy/EnemyMovement.cs

@@ -1,32 +1,0 @@
-﻿using UnityEngine;
-using System.Collections;
-
-public class EnemyMovement : MonoBehaviour
-{
-    Transform player;
-    PlayerHealth playerHealth;
-    EnemyHealth enemyHealth;
-    UnityEngine.AI.NavMeshAgent nav;
-
-
-    void Awake ()
-    {
-        player = GameObject.FindGameObjectWithTag ("Player").transform;
-        playerHealth = player.GetComponent <PlayerHealth> ();
-        enemyHealth = GetComponent <EnemyHealth> ();
-        nav = GetComponent <UnityEngine.AI.NavMeshAgent> ();
-    }
-
-
-    void Update ()
-    {
-        if(enemyHealth.currentHealth > 0 && playerHealth.currentHealth > 0)
-        {
-            nav.SetDestination (player.position);
-        }
-        else
-        {
-           nav.enabled = false;
-        }
-    }
-}

### 2018-12-04 Unity/Assets/Scripts/Player/PlayerMovement.cs

@@ -1,60 +1,0 @@
-﻿using UnityEngine;
-
-public class PlayerMovement : MonoBehaviour
-{
-    public float speed = 6f;
-
-    Vector3 movement;
-    Animator anim;
-    Rigidbody playerRigidbody;
-    int floorMask;
-    float camRayLength = 100f;
-
-    void Awake()
-    {
-        floorMask = LayerMask.GetMask("Floor");
-        anim = GetComponent<Animator>();
-        playerRigidbody = GetComponent<Rigidbody>();
-    }
-
-    void FixedUpdate()
-    {
-        float h = Input.GetAxisRaw("Horizontal");
-        float v = Input.GetAxisRaw("Vertical");
-
-        Move(h, v);
-        Turning();
-        Animating(h, v);
-    }
-
-    void Move(float h, float v)
-    {
-        movement.Set(h, 0f, v);
-
-        movement = movement.normalized * speed * Time.deltaTime;
-
-        playerRigidbody.MovePosition(transform.position + movement);
-    }
-
-    void Turning()
-    {
-        Ray camRay = Camera.main.ScreenPointToRay(Input.mousePosition);
-
-        RaycastHit floorHit;
-
-        if(Physics.Raycast(camRay, out floorHit, camRayLength, floorMask))
-        {
-            Vector3 playerToMouse = floorHit.point - transform.position;
-            playerToMouse.y = 0f;
-
-            Quaternion newRotation = Quaternion.LookRotation(playerToMouse);
-            playerRigidbody.MoveRotation(newRotation);
-        }
-    }
-
-    void Animating(float h, float v)
-    {
-        bool walking = h != 0f || v != 0f;
-        anim.SetBool("IsWalking", walking);
-    }
-}

### 2018-12-04 paper.tex
Paper: musings on what is to come

@@
 \section{Preliminary Results and Discussion}
-Over the course of this project, we learned more about game design than we did evolutionary algorithms and artificial life.
-The majority of our time working on this project was spent dealing with learning the basics of Unity and C\#, which presented a very significant challenge that we vastly underestimated.
+Over the course of this project, we learned more about game design than we did
+evolutionary algorithms and artificial life. The majority of our time working on
+this project was spent dealing with learning the basics of Unity and C\#, which
+presented a very significant challenge that we vastly underestimated.
 
@@
 strategies.
+
+One approach to solving this problem could be moving towards more complicated
+models of selection and reproduction than our current keep \(n\) percent,
+asexually reproduce the best genomes and then do a straight pass of mutation.
+Moving to a system where reproductive resources are distributed according to the
+Z-score (standard deviations from the mean) or similar of fitness that give more
+reproductive power to individual that more drastically improve on the status quo
+could allow for a system that reacts more strongly to change. Another option
+could be coding part of the mutation rate in genomes to allow evolution to
+determine it's own speed. The two previous approaches could even be combined for
+as dynamic an evolution environment as possible.
+
+Sexual (genderless) reproduction could also be introduced as a way of trying to
+increase diversity. Plain sexual reproduction without any further restrictions
+could allow good traits that evolve in parallel to be combined into a single
+individual with the benefits of both, which has fairly obvious advantages.
+This simple approach to sexual reproduction could, however, force a single
+species to dominate quickly depending on how well neural net parameters combine,
+as it could easily be the case that two disparately evolving neural nets combine
+into a total dud, despite having fit parents. One way around that would be to
+condition reproduction on similarity, such genomes are more likely to reproduce
+with those that are structurally similar. Another approach would be to allow
+genomes to determine mating preference based on other genomes' content and
+fitness, and then run them through a tournament to determine mates. This would
+have the additional benefit of allowing additional emergent behavior that has
+not been conceived of in this speculation.
+
+Conceptually, evolving neural nets has the massive benefit of not worrying about
+how to differentiate and nicely back-propagate
+
+individuals that jump out ahead of the population could
+
+Discussion: talk about the lack of direction vectors being fed into the neural nets.
 

### 2018-12-04 paper.tex
Expanded introduction and background

--- 2018-12-04 paper.tex
@@
 
+\usepackage [english]{babel}
+\usepackage [autostyle, english = american]{csquotes}
+\MakeOuterQuote{"}
 \usepackage{natbib,alifeconf}  %% The order is important
 \usepackage{url}
+\usepackage{graphicx}
+\graphicspath{ {./pictures/} }
+
+\def\imfig#1#2{\begin{figure}[h] \centering \includegraphics[width=\columnwidth]{#1} \caption{#2} \end{figure}}
 
@@
 \tavs~is a real-time tower defense game with evolving enemies; which is to say that the player places down towers and other defenses in real time to fend off waves of enemies attempting to destroy the player's "home base." In typical tower defense games, after killing one group of enemies, another comes which is usually stronger than the previous, due to a pre-ordained set of constraints.
-\textit{They are Very Smart} differs from typical tower defense games in that enemy progression is not determined by divine force (i.e., the game developer), but rather evolves as a result of a genetic algorithm which controls the enemies' damage, movement speed, health, and navigation.
+\tavs~differs from typical tower defense games in that enemy progression is not determined by the game developer, but rather evolves as a result of a genetic algorithm which controls the enemies' damage, movement speed, health, and navigation.
+
+\begin{figure}[h]
+	\includegraphics[width=\columnwidth]{InGameLabeled}
+	\caption{A screenshot from the game, with various elements labeled}
+\end{figure}
+
+In \tavs, player interaction consists of constructing defenses around a central home base.
+The home base exists in a fixed location in the center of the map, has a set maximum health, and can be damaged by attacks from enemies.
+Waves of enemies will spawn indefinitely and attempt to destroy the home base.
+When the health of the home base reaches zero, the game ends.
+
+Players begin the game with an initial sum of money, which can be used to purchase defenses from the tower construction UI (see Figure 1).
+Defenses are damageable structures which the player may place on any unoccupied square within the defense placement grid.
+\imfig{ZoomedOut}{The initial state of the game, showing the home base in the middle of the defense placement grid}
+
+Defenses provide various benefits to the player, such as physically blocking the path of enemies or actively damaging enemies with projectile-based attacks. Some examples of defenses include:
+\begin{itemize}
+	\item Walls (vertical/horizontal) - inexpensive defenses which block the path of enemies
+	\item Machine gun turrets - towers which fire damaging projectiles at nearby enemies
+	\item Energy pylons - fragile towers which deal no damage, but instead passively generate income for the player
+\end{itemize}
+
+Defenses cost money, which may be gained by killing attacking enemies.
+As the game progresses, the player may fortify their base by purchasing more expensive defenses and designing complex arrangements of walls and towers in order to thwart enemies.
+
+In \tavs, the player must defend their home base against the aforementioned onslaught of enemies such as the fearsome Zombunny (see Figure 3).
+Zombunnies are driven by a single goal: destruction of the player's home base.
+Zombunnies spawn in groups of ten (separated by a slight delay) at the beginning of the game.
+Subsequent waves spawn after all members from the previous wave have died.
+Zombunnies use a genetic algorithm in conjunction with a recurrent neural network to evolve a pathfinding algorithm between generations (waves), with the long-term incentive of dealing damage to the player's base (explain fitness criteria more concisely here).
+Zombunnies can be killed by either taking damage from a player's defenses or through "starvation." A Zombunny will starve to death if it does not take or deal damage for a given length of time.
+Through this mechanism, those Zombunnies which survive the longest will be those that interact the most with the player's defenses, and will be more likely to pass on their Zombunnies have stats , when they are born, Zombunnies are assigned can "see" nearby entities, including other Zombunnies and
+
+\imfig{ZombunnyColliders}{A Zombunny, with attacker and damage colliders highlighted}
+
+Zombunnies - Health decay (starvation) - Basic vision->vector overview
 
@@
 
-\tavs was initially inspired by Numantian Games' \textit{They Are Billions}, a game in which a player must build defenses in order to fend off a zombie apocalypse.
+\tavs~was initially inspired by Numantian Games' \textit{They Are Billions}, a game in which a player must build defenses in order to fend off a zombie apocalypse.
 The game features massive numbers of zombies.
@@
 The result is significantly pared down in comparison, as the focus has been on zombie evolution as opposed to player interactivity and enjoyability.
-However, similiarities to \textit{They Are Billions} can be seen in the resource management system, the player's defense of a citadel, and need to fend off the faceless hordes.
-\textit{They Are Billions} puts additional emphasis on world generation, player exploration, and narrative elements.
+However, similarities to \textit{They Are Billions} can be seen in the resource management system, the player's defense of a citadel, and need to fend off the faceless hordes.
+In contrast, \textit{They Are Billions} puts additional emphasis on world generation, player exploration, and narrative elements.
 
@@
 NEAT is particularly applicable to our issue because it allows the evolution of different topologies and weights in neural networks at the same time, unlike standard back-propagation learning, and is also well-suited for encoding into a genome for evolution.
-NEAT works essentially by encoding a function that then generates a neural net (citation needed), starting out with low complexity of topology, which can then evolve towards more complex topologies.
+NEAT works by encoding a function that then generates a neural net (citation needed), starting out with low complexity of topology, which can then evolve towards more complex topologies.
 
@@
 In the future, we would experiment with elements such as variable damage output from towers and other defenses (so as to avoid the aforementioned numeric minima and maxima), as well as coming up with ways to encourage attacking the player's base more as time goes on.
-
-Ultimately, we think that although evolution was the appropriate mechanism to to solve the issue at hand, game development was not the appropriate environment for this topic, given the time investment.
+\begin{figure}
+	\includegraphics[width=\columnwidth]{InGame2}
+	\caption{An in-game image}
+\end{figure}
 
@@
 
-\section{Acknowledgements}
+\section{Acknowledgments}
 \begin{itemize}

### 2018-12-04 paper.tex

@@
 \section{Preliminary Results and Discussion}
-Over the course of this project, we learned more about game design than we did evolutionary algorithms and artificial life.
-The majority of our time working on this project was spent dealing with learning the basics of Unity and C\#, which presented a very significant challenge that we vastly underestimated.
+Over the course of this project, we learned more about game design than we did
+evolutionary algorithms and artificial life. The majority of our time working on
+this project was spent dealing with learning the basics of Unity and C\#, which
+presented a very significant challenge that we vastly underestimated.
 
-At this time, we are currently waiting on actual results from our project, but we hope that given a large enough population of zombies, we might see populations of zombies evolving to counteract players' strategies, although we may also see players coming up with ways to counteract the zombies by exploiting elements of the fitness function and construction system in ways unforeseen, possibly by playing in such a way as to allow the zombies to optimize for something other than killing the player's home base.
-Another possibility we might expect to see is the development of swarm or anti-swarm behavior based on the effectiveness of player defenses, as well as zombies possibly hitting minima or maxima depending on hard-coded numbers in the game environment.
+At this time, we are currently waiting on actual results from our project, but
+we hope that given a large enough population of zombies, we might see
+populations of zombies evolving to counteract players' strategies. Evolution
+will likely have little trouble tackling a trivial or consistent player
+strategy, like consistently rebuilding the same towers in the same place and
+relying heavily on a single tower type, but evolution may have trouble keeping
+up with a player that consistently changes strategy over the course of the game.
+Our system of softmaxing the genome speed, health, and damage could also
+result in progressively larger values relative to the mutation rate, making it
+hard for long-evolved values to be changed in the face of changing player
+strategies.
 
-In the future, we would experiment with elements such as variable damage output from towers and other defenses (so as to avoid the aforementioned numeric minima and maxima), as well as coming up with ways to encourage attacking the player's base more as time goes on.
-\begin{figure}
-	\includegraphics[width=\columnwidth]{InGame2}
-	\caption{An in-game image}
-\end{figure}
+One approach to solving this problem could be moving towards more complicated
+models of selection and reproduction than our current keep \(n\) percent,
+asexually reproduce the best genomes and then do a straight pass of mutation.
+Moving to a system where reproductive resources are distributed according to the
+Z-score (standard deviations from the mean) or similar of fitness that give more
+reproductive power to individual that more drastically improve on the status quo
+could allow for a system that reacts more strongly to change. Another option
+could be coding part of the mutation rate in genomes to allow evolution to
+determine it's own speed. The two previous approaches could even be combined for
+as dynamic an evolution environment as possible.
+
+Sexual (genderless) reproduction could also be introduced as a way of trying to
+increase diversity. Plain sexual reproduction without any further restrictions
+could allow good traits that evolve in parallel to be combined into a single
+individual with the benefits of both, which has fairly obvious advantages.
+This simple approach to sexual reproduction could, however, force a single
+species to dominate quickly depending on how well neural net parameters combine,
+as it could easily be the case that two disparately evolving neural nets combine
+into a total dud, despite having fit parents. One way around that would be to
+condition reproduction on similarity, such genomes are more likely to reproduce
+with those that are structurally similar. Another approach would be to allow
+genomes to determine mating preference based on other genomes' content and
+fitness, and then run them through a tournament to determine mates. This would
+have the additional benefit of allowing additional emergent behavior that has
+not been conceived of in this speculation.
+
+Conceptually, evolving neural nets has the massive benefit of not worrying about
+how to differentiate and nicely back-propagate
+
+individuals that jump out ahead of the population could
+
+Discussion: talk about the lack of direction vectors being fed into the neural nets.
+
+may also see players coming up with ways to counteract the zombies by exploiting
+elements of the fitness function and construction system in ways unforeseen,
+possibly by playing in such a way as to allow the zombies to optimize for
+something other than killing the player's home base. Another possibility we
+might expect to see is the development of swarm or anti-swarm behavior based on
+the effectiveness of player defenses, as well as zombies possibly hitting minima
+or maxima depending on hard-coded numbers in the game environment.
+
+In the future, we could experiment with elements such as variable damage output
+from towers and other defenses (so as to avoid the aforementioned numeric minima
+and maxima), as well as coming up with ways to encourage attacking the player's
+base more as time goes on; this could include ways
 

### 2018-12-05 paper.tex
Completed introduction

@@
 
+\pagebreak
 In \tavs, the player must defend their home base against the aforementioned onslaught of enemies such as the fearsome Zombunny (see Figure 3).
@@
 Zombunnies can be killed by either taking damage from a player's defenses or through "starvation." A Zombunny will starve to death if it does not take or deal damage for a given length of time.
-Through this mechanism, those Zombunnies which survive the longest will be those that interact the most with the player's defenses, and will be more likely to pass on their Zombunnies have stats , when they are born, Zombunnies are assigned can "see" nearby entities, including other Zombunnies and
+Through this starvation mechanism, the Zombunnies which survive the longest are ultimately those which interact the most with the player's defenses, and are subsequently more likely to pass on attributes of their genome to the next generation.
+Zombunnies have three characteristic attributes: health, damage, and movement speed.
+All three of these stats are assigned upon spawning as dictated by their genome.
+Pathfinding is controlled by a recurrent neural net, whose weights are determined through a genetic algorithm between waves, which optimizes for Zombunnies' ability to achieve their overarching goal of player base destruction.
+Zombunnies can "see" nearby entities within a certain radius, including other Zombunnies, player defenses, and the player's home base (when in range).
+Based on the combination of visible inputs, Zombunnies will output a chosen direction which they will then walk in.
+This algorithm updates on a tick-by-tick basis.
+Zombunnies will damage structures they collide with.
+Because evolution of the pathfinding neural net only happens between generations, near the beginning of the game, Zombunnies will start off with relatively stupid pathfinding which will typically cause the first few populations to starve to death without dealing any significant damage.
+This provides the player with an initial grace period during which they may build their initial defenses.
+As time goes on, Zombunnies will evolve towards an optimal stat distribution of health, damage, and speed, as well as in their ability to pathfind in such a way as to thwart the player's defenses and end the game.
 
@@
 
-Zombunnies - Health decay (starvation) - Basic vision->vector overview
-
-\begin{itemize}
-    \item Description of tower-defense UI
-    \item Placement of walls vs. towers
-    \item "Spawn points" for zombies
-    \item Central defensible location
-    \item Economy
-    \item Game end/lack thereof
-\end{itemize}
+%overview
+%\begin{itemize}
+%    \item Description of tower-defense UI
+%    \item Placement of walls vs. towers
+%    \item "Spawn points" for zombies
+%    \item Central defensible location
+%    \item Economy
+%    \item Game end/lack thereof
+%\end{itemize}
 

### 2018-12-05 paper.tex
Conclusion, and fix long url

--- 2018-12-04 paper.tex
@@
 scene is then located at
-\texttt{They-Are-Very-Smart/TD/TowerDefence/Assets/Scenes/Levels/Level0/Level0.unity}
+\url{They-Are-Very-Smart/TD/TowerDefence/Assets/Scenes/Levels/Level0/Level0.unity}
 Double clicking on this file on any computer with unity installed will open up
@@
 
-At this time, we are currently waiting on actual results from our project, but
-we hope that given a large enough population of zombies, we might see
+At this time, we are waiting on actual results from our project.
+We hope that given a large enough population of zombies, we might see
 populations of zombies evolving to counteract players' strategies. Evolution
 will likely have little trouble tackling a trivial or consistent player
-strategy, like consistently rebuilding the same towers in the same place and
-relying heavily on a single tower type, but evolution may have trouble keeping
-up with a player that consistently changes strategy over the course of the game.
+strategy, like rebuilding the same towers in the same place and
+relying heavily on a single tower type, but may have trouble keeping
+up with a player that constantly changes strategy over the course of the game.
 Our system of softmaxing the genome speed, health, and damage could also
 result in progressively larger values relative to the mutation rate, making it
-hard for long-evolved values to be changed in the face of changing player
-strategies.
+hard for long-evolved high speed value to be traded for damage in the face of
+changing player strategies.
 
-One approach to solving this problem could be moving towards more complicated
+Zombunnies will likely evolve around quirks in the way the
+game is organized. The primary example would be having health that is just above
+multiples of tower damage, allowing it to sustain an additional hit with
+insignificant investment in the health stat. This particular problem could be
+solved by having towers deal damage with slight randomness, but there likely
+exist similar problems that have not been considered.
+
+Players, on the other hand, may also learn to optimize around our implementation
+of evolution. Conceivably clever player could develop two very different
+strategies ahead of time. The player would first implement the weaker strategy,
+and as soon as the zombunnies have deeply rooted themselves in the local maximum
+versus that strategy, the strategy could be changed to the second strategy,
+leaving the zombunnies unable to easily adapt to the new strategy.
+
+Solving these problems would probably involve moving towards more complicated
 models of selection and reproduction than our current keep \(n\) percent,
@@
 
-Conceptually, evolving neural nets has the massive benefit of not worrying about
-how to differentiate and nicely back-propagate
+Conceptually, evolving neural nets instead of using backpropagation
+has the massive benefit of not worrying about how to differentiate and nicely
+back-propagate the reward/fitness function to learn, which opens up the
+possibility to drop in a nerual net to replace any function in a learning
+environment; on a larger timescale, the selection tournament process itself
+could modeled with a recurrent neural network, and evolved over multiple plays
+of the game.
 
-individuals that jump out ahead of the population could
-
-Discussion: talk about the lack of direction vectors being fed into the neural nets.
-
-may also see players coming up with ways to counteract the zombies by exploiting
-elements of the fitness function and construction system in ways unforeseen,
-possibly by playing in such a way as to allow the zombies to optimize for
-something other than killing the player's home base. Another possibility we
-might expect to see is the development of swarm or anti-swarm behavior based on
-the effectiveness of player defenses, as well as zombies possibly hitting minima
-or maxima depending on hard-coded numbers in the game environment.
-
-In the future, we could experiment with elements such as variable damage output
-from towers and other defenses (so as to avoid the aforementioned numeric minima
-and maxima), as well as coming up with ways to encourage attacking the player's
-base more as time goes on; this could include ways
+Allowing the zombunnies to keep track of what they learn from game to game could
+be useful as a ``hard mode'' should the base game be too easy, perhaps with the
+additional information passed to the navigation function of the round. In an actual game
+using this technology to evolve AI, this could be expanded to the entire
+playerbase training a single pathfinding algorithm that is then redistributed to
+each client, and perhaps even takes in all previous player game history as
+additional input. The missing backpropagation requirement opens up
+any function to becoming an neural net, and with any input.
 

### 2018-12-05 TD/TowerDefense/Assets/Scripts/Core/Health/DamageableBehaviour.cs
Clean up scripts

@@ -52,7 +52,7 @@ namespace Core.Health
 		/// <param name="damageValue">Damage value.</param>
 		/// <param name="damagePoint">Damage point.</param>
 		/// <param name="alignment">Alignment value</param>
-		public virtual void TakeDamage(float damageValue, Vector3 damagePoint, IAlignmentProvider alignment)
+		public virtual float TakeDamage(float damageValue, Vector3 damagePoint, IAlignmentProvider alignment)
 		{
 			HealthChangeInfo info;
 			configuration.TakeDamage(damageValue, alignment, out info);
@@ -61,6 +61,7 @@ namespace Core.Health
 			{
 				hit(damageInfo);
 			}
+            return damageInfo.healthChangeInfo.absHealthDifference;
 		}
 
 		protected virtual void Awake()

### 2018-12-05 TD/TowerDefense/Assets/Scripts/Evolution/Genome.cs

@@ -9,14 +9,15 @@ namespace Evolution
 {
     public class Genome
     {
-        private readonly static int HEALTH_SCALE = 1;
-        private readonly static int DAMAGE_SCALE = 1;
+        private readonly static float HEALTH_SCALE = 1;
+        private readonly static float DAMAGE_SCALE = 1;
         private readonly static float MOVEMENT_SCALE = 0.4f;
         
         private static int current_id = 0;
 
         private static int id_counter = 0;
 
+        // ID # Makes sure that all genomes hash differently
         private int id;
         public int Id
         {
@@ -29,7 +30,7 @@ namespace Evolution
         // TODO: Use SoftMax for these distributions
 
         private float health;
-        public float Health { 
+        public float Health {
             get {
                 return HEALTH_SCALE * (1 + health) * divisor;
             }
@@ -43,7 +44,7 @@ namespace Evolution
         }
 
         private float movementSpeed;
-        public float MovementSpeed { 
+        public float MovementSpeed {
             get {
                 return MOVEMENT_SCALE * (1 + movementSpeed) * divisor;
             }
@@ -90,7 +91,12 @@ namespace Evolution
 
         public Genome mutate(ZigguratGaussianSampler sampler, float difficultyModifier)
         {
-            return new Genome(health + sampler.Sample(), damage + sampler.Sample(), movementSpeed + sampler.Sample(), this.totalStats + difficultyModifier);
+            return new Genome(
+                health + sampler.Sample(), 
+                damage + sampler.Sample(), 
+                movementSpeed + sampler.Sample(), 
+                this.totalStats + difficultyModifier
+                );
         }
 
         /// <summary>
@@ -102,7 +108,12 @@ namespace Evolution
         /// <param name="health">current health of the zombie</param>
         /// <param name="nearby">dictionary from nearby entities mapped to the vector to them</param>
         /// <returns>direction, The direction to move in</returns>
-        public float CalculateDirection(PolarVector previous_direction, int time_alive, float health, Dictionary<Targetable, PolarVector> nearby)
+        public float CalculateDirection(
+            PolarVector previous_direction, 
+            int time_alive, 
+            float health, 
+            Dictionary<Targetable, PolarVector> nearby
+            )
         {
             return 0f;
         }

### 2018-12-05 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAgent.cs

@@ -18,22 +18,18 @@ namespace TowerDefense.Agents
         private readonly static float SINK_SPEED = 2.5f;
         private readonly static float SINK_TIME = 2.0f;
 
-        private float speed;
-
         public override Vector3 velocity
         {
             // Previous velocity set by Neural Net
             get { return lastVelocity.toVector3(); }
         }
         private PolarVector lastVelocity;
-        
-        protected LevelManager m_LevelManager;
 
         public double Fitness {
-            get;
-            protected set;
+            get { return this.damageDone; }
         }
 
+        // Set of nearby objects
         private HashSet<Targetable> inVision;
 
         public readonly IAlignmentProvider alignment;
@@ -43,11 +39,14 @@ namespace TowerDefense.Agents
         public Rigidbody rigidBody;
         public Animator anim;
 
+        private int time_alive = 0;
+        private float time_dead = 0;
         private bool myIsDead = false;
         // For debug purposes only
         public float CurrentHealth = 0.1f;
         protected float damageDone = 0;
-
+        
+        // Increment total damage done over a zombie's lifetime
         public void addDamageDone(float increment)
         {
             this.damageDone += increment;
@@ -62,7 +61,6 @@ namespace TowerDefense.Agents
             }
             set
             {
-                //this.lastVelocity = PolarVector.fromVector3(transform.rotation.eulerAngles);
                 lastVelocity = new PolarVector(270);
                 genome = value;
                 var health = genome.Health;
@@ -72,8 +70,6 @@ namespace TowerDefense.Agents
                 genome = value;
             }
         }
-        private int time_alive = 0;
-        private float time_dead = 0;
 
         protected override void Awake()
         {
@@ -129,7 +125,7 @@ namespace TowerDefense.Agents
             }
             time_alive += 1;
 
-            // Find path to nearby objects
+            // Find relative position of nearby objects
             var nearbyDict = new Dictionary<Targetable, PolarVector>();
             foreach(var item in inVision)
             {

### 2018-12-05 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAttacker.cs

@@ -7,14 +7,14 @@ using UnityEngine;
 [RequireComponent(typeof(Collider))]
 public class ZombieAttacker : MonoBehaviour {
 
-   public ZombieAgent ZombieAgent;
+   public ZombieAgent zombieAgent;
 
     private HashSet<Targetable> toAttack;
 
     // Use this for initialization
     void Start()
     {
-        ZombieAgent = GetComponentInParent<ZombieAgent>();
+        zombieAgent = GetComponentInParent<ZombieAgent>();
         toAttack = new HashSet<Targetable>();
     }
 
@@ -31,18 +31,18 @@ public class ZombieAttacker : MonoBehaviour {
 
     private void Update()
     {
-        foreach (var item in toAttack)
+        foreach (Targetable item in toAttack)
         {
             if (item != null)
             {
-                var health = item.configuration.currentHealth;
-                item.TakeDamage(
-                    ZombieAgent.Genome.Damage * Time.deltaTime,
-                    ZombieAgent.transform.position,
-                    ZombieAgent.configuration.alignmentProvider
+                float health = item.configuration.currentHealth;
+                float damage = item.TakeDamage(
+                    zombieAgent.Genome.Damage * Time.deltaTime,
+                    zombieAgent.transform.position,
+                    zombieAgent.configuration.alignmentProvider
                 );
-
-                this.ZombieAgent.addDamageDone(health - item.configuration.currentHealth);
+                zombieAgent.addDamageDone(damage);
+                this.zombieAgent.addDamageDone(health - item.configuration.currentHealth);
             }
         }
     }

### 2018-12-05 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/GenomeManager.cs

@@ -43,7 +43,6 @@ namespace TowerDefense.Level
         // TODO
         private Stack<Genome> toSpawn;
         private ZombieAgent prefabAgent;
-
         private ZigguratGaussianSampler sampler;
 
         private void Start()
@@ -75,7 +74,7 @@ namespace TowerDefense.Level
                 if (pair.Key == null) continue;
                 nextWave.Push(pair.Key.mutate(sampler, GROWTH_RATE));
             }
-            //Possibly scramble list here?
+            // Scramble list here
 
             //Reset values
             remaining_alive = POPULATION_SIZE;
@@ -83,7 +82,6 @@ namespace TowerDefense.Level
             genomeMaps.Add(newMap);
             currentMap = genomeMaps[genomeMaps.Count - 1];
 
-            //TODO
             toSpawn = nextWave;
 
             //Spawn next wave
@@ -98,7 +96,6 @@ namespace TowerDefense.Level
             }
             int spawn_index = Random.Range(0, SpawnPoints.Count);
 
-            // TODO: Figure out pools!
             var prefabInstance = Instantiate(ZombiePrefab, SpawnPoints[spawn_index]);
             var agentInstance = prefabInstance.GetComponent<ZombieAgent>();
             agentInstance.Genome = toSpawn.Pop();

### 2018-12-05 paper.tex
Working on tutorial

@@
 \def\imfig#1#2{\begin{figure}[h] \centering \includegraphics[width=\columnwidth]{#1} \caption{#2} \end{figure}}
+\def\imfigB#1#2{\begin{figure} \centering \includegraphics[width=\columnwidth]{#1} \caption{#2} \end{figure}}
+\def\imfigH#1#2{\begin{figure}[H] \centering \includegraphics[width=\columnwidth]{#1} \caption{#2} \end{figure}}
 
@@
 \pagebreak
+
+\imfig{BaseExample}{An example set of player defenses around the home base}
 In \tavs, the player must defend their home base against the aforementioned onslaught of enemies such as the fearsome Zombunny (see Figure 3).
@@
 \section{Background}
-In \tavs, we utilize a basic genetic algorithm to train a recurrent neural network generated using the Neuroevolution of Augmenting Topologies (NEAT) method, ~cite http://sharpneat.sourceforge.net/~ with https://www.heatonresearch.com/encog/, which is a generalized deep-learning library that includes implementations of NEAT and HyperNEAT.
+In \tavs, we utilize a basic genetic algorithm to train a recurrent neural network generated using the Neuroevolution of Augmenting Topologies (NEAT) method and \href{https://www.heatonresearch.com/encog/}{Encog} framework, which can be found \href{https://sharpneat.sourceforge.net/}{here}, which is a generalized deep-learning library that includes implementations of NEAT and HyperNEAT.
 
 NEAT is particularly applicable to our issue because it allows the evolution of different topologies and weights in neural networks at the same time, unlike standard back-propagation learning, and is also well-suited for encoding into a genome for evolution.
-NEAT works by encoding a function that then generates a neural net (citation needed), starting out with low complexity of topology, which can then evolve towards more complex topologies.
-
-Insert helpful diagram here
+NEAT works by encoding a function that then generates a neural net, starting out with low complexity of topology, which can then evolve towards more complex topologies.
 
@@
 \href{https://github.com/YourFin/They-Are-Very-Smart}{github.com/yourfin/They-Are-Very-Smart},
-and downloaded with a standard \texttt{git clone} command. The relevant unity
+and downloaded with a standard \texttt{git clone} command. The relevant Unity
 scene is then located at
-\url{They-Are-Very-Smart/TD/TowerDefence/Assets/Scenes/Levels/Level0/Level0.unity}
-Double clicking on this file on any computer with unity installed will open up
-the unity editor with the context for this paper.
+\path{They-Are-Very-Smart/TD/TowerDefence/Assets/Scenes/Levels/Level0/Level0.unity}
+Double clicking on this file on any computer with Unity installed will open up
+the Unity editor with the context for this paper.
 
-Overview
-\begin{itemize}
-    \item Unity
-    \item Tower Defense tutorial
-    \item Action Game Framework
-    \item Creating custom towers
-    \item Custom scripts
-        \begin{itemize}
-            \item Genome
-            \item ZombieAgent
-            \item GenomeManager
-            \item ZombieAttacker
-        \end{itemize}
-    \item Problems importing packages
-    \item Relevant parts of Encog framework
-        \begin{itemize}
-            \item Manually pulling out Encog training methods for neural nets
-            \item Stealing Softmax function
-        \end{itemize}
-    \item Point array stats system
-    \item Details of genetic algorithm
-        \begin{itemize}
-            \item Mutation
-            \item Keeping track of fitness
-            \item Population management
-            \item Starvation function
-        \end{itemize}
-\end{itemize}
+\subsection{Code overview}
+\subsubsection{PolarVector}
+The PolarVector class encapsulates the internal representation that we use for storing and passing vectors to the neural net, as well as keeping track of the previous direction a Zombunny was headed during the previous tick.
+The PolarVector class essentially wraps a float, direction (in degrees) and a float, magnitude, which provides sufficient information to create a new vector in two-dimensional space.
+The PolarVector class provides some convenient helper methods for converting between Cartesian and Polar coordinate systems, as the Unity engine primarily uses Cartesian coordinates.
+
+\imfigB{PolarVector1}{The basics of PolarVector}
+
+The implementation details of PolarVector's conversion functions are fairly trivially derived from math, but it should be noted that all Cartesian components are encoded as Vector3 components as the game takes place on the X-Z plane (see Figure 6).
+
+\imfigB{PolarVector2}{Conversion functions for PolarVector}
+
+\subsubsection{Genome}
+The Genome class encapsulates the data that is stored on a genome-by-genome basis, and provides most of the procedures that deal with their mutation, as well as providing conversions from their internal state to the game-useful health, speed, and damage values, as well as providing an interface to conveniently call the resulting pathfinding neural net.
+
+\imfigB{Genome1}{Constants and Id for the Genome class}
+
+In Figure 7, we can see the constants that are used to scale a Zombunny's health, movement speed, and damage, which need to be set manually.
+The Id field is used as a unique identifier if genomes need to be looked up, and also ensures that every genome will hash differently.
+
+\imfig{Mutation}{Mutation procedure of the Genome class}
+
+The mutation function in Figure 8 essentially creates a new copy of the current genome, nudged by normally distributed random numbers.
+
+\subsubsection{GenomeManager}
+
+The GenomeManager class keeps track of game-wide genome management, i.e.
+selection and reproduction, as well as spawning Zombunnies and initiating new waves.
+The GenomeManager holds onto a collection of all genomes in a wave-by-wave list of hashmaps that map genomes to their fitness.
+The primary properties of the GenomeManager class can be seen in Figure 9, with various hardcoded constants that can be adjusted to influence general properties of the evolution, as well as the genomeMaps object, which contains the aforementioned collection of all genomes used in the course of evolution thus far.
+
+\imfig{GenomeManagerProperties}{Properties of the GenomeManager class}
+
+The initialization process of GenomeManager (see Figure 10) consists primarily of allocating the containing data structures for the various stages of the genome life cycle, followed by creating a first wave with randomized genomes and zero fitness.
+It should also be noted that we initialize our ZigguratGaussianSampler here from the Redzen library, which provides a fast way of generating normally-distributed floating-point numbers.
+
+\imfig{GenomeManagerInit}{The GenomeManager initialization process}
+
+Figure 11 shows the NextWave function, which handles the wave-to-wave portions of evolution, i.e.
+culling and reproduction.
+It should also be noted that we scramble the Zombunnies, as the Zombunnies get spawned in the order in which they are placed onto the nextWave stack.
+We scramble the order of the genomes between waves to make sure that evolution doesn't get held up by some side effect of consistent ordering.
+
+\imfig{GenomeManagerNextWave}{The NextWave method of GenomeManager}
+
+The Spawn method, as seen in Figure 12, is called every SPAWN\_DELAY interval POPULATION\_COUNT times.
+The function starts by spawning a Zombunny with no genome due to the inability to provide parameters upon GameObject instantiation.
+Therefore, we set the genome after the fact, popping it off of the toSpawn stack, also adding the ZombieDied function to the removed event on said Zombunny, which allows us to execute code in the context of the GenomeManager upon Zombunny death; namely, ZombunnyDied.
+ZombunnyDied handles finding the fitness of Zombunnies and adding them to the list of completed genomes, as well as calling NextWave again when the last Zombunny in the wave dies.
+
+\imfig{GenomeManagerSpawn}{Spawning machinery of the GenomeManager class}
+
+\subsubsection{Redzen}
+Redzen is a general-purpose utilities library for C\# that contains the fast random function that we use.
+However, it should be noted that the library as it may be found online at the time of writing does not compile with the older C\# compiler that Unity uses.
+Thus, we had to manually delete most of the library files and remove underscore digit separators from some numeric constants, as they are a C\# 7 feature.
+You can find our compatible library at \path{They-Are-Very-Smart/TD/TowerDefense/Assets/Scripts/Util/Redzen}
+
+\subsubsection{}
+
+%Overview
+%\begin{itemize}
+%    \item Unity
+%    \item Tower Defense tutorial
+%    \item Action Game Framework
+%    \item Creating custom towers
+%    \item Custom scripts
+%        \begin{itemize}
+%            \item Genome
+%            \item ZombieAgent
+%            \item GenomeManager
+%            \item ZombieAttacker
+%        \end{itemize}
+%    \item Problems importing packages
+%    \item Relevant parts of Encog framework
+%        \begin{itemize}
+%            \item Manually pulling out Encog training methods for neural nets
+%            \item Stealing Softmax function
+%        \end{itemize}
+%    \item Point array stats system
+%    \item Details of genetic algorithm
+%        \begin{itemize}
+%            \item Mutation
+%            \item Keeping track of fitness
+%            \item Population management
+%            \item Starvation function
+%        \end{itemize}
+%\end{itemize}
 
@@
 strategies ahead of time. The player would first implement the weaker strategy,
-and as soon as the zombunnies have deeply rooted themselves in the local maximum
+and as soon as the Zombunnies have deeply rooted themselves in the local maximum
 versus that strategy, the strategy could be changed to the second strategy,
-leaving the zombunnies unable to easily adapt to the new strategy.
+leaving the Zombunnies unable to easily adapt to the new strategy.
 
@@
 
-Allowing the zombunnies to keep track of what they learn from game to game could
+Allowing the Zombunnies to keep track of what they learn from game to game could
 be useful as a ``hard mode'' should the base game be too easy, perhaps with the
@@
         \item Redzen repository for normal random numbers
-        \item
     \end{itemize}

### 2018-12-09 paper.tex
work on ZombieAgent tutorial section

@@
 \subsubsection{Redzen}
+
 Redzen is a general-purpose utilities library for C\# that contains the fast random function that we use.
@@
 
-\subsubsection{}
+\subsubsection{ZombieAgent}
+
+ZombieAgent is a GameObject which determines Zombunny behavior and stats from a genome and keeps track of fitness for each individual Zombunny.
+To do so, ZombieAgent pulls all the stat-determining values from the genome and applies them upon instantiation, i.e.
+setting health, damage, and speed as determined by the genome, as well as handling tick-to-tick operations during a Zombunny's lifetime.
+These tick-to-tick operations include choosing the next movement vector based on the location of nearby GameObjects and agent's current status.
+
+\imfig{ZombieAgent1}{ZombieAgent class parameters}
+
+In Figure 13, observe that the ZombieAgent class inherits from the Targetable class.
+Targetable is the parent class for every GameObject in the Action Game Framework, which can be automatically fired upon by ranged weapons, i.e.
+targeted.
+This also allows any existing defenses from the default game or any other targeting GameObject from the Action Game Framework to work without extra compatibility code.
+SINK\_SPEED and SINK\_TIME are constants used for death animation.
+velocity provides the Zombunny's current velocity for any consumers of the Targetable parent class.
+LastVelocity stores the previous movement vector as a PolarVector, in a format more congenial to the pathfinding algorithm.
+Fitness is an interface used to grab the effectiveness of this ZombieAgent at the end of its lifespan by the GenomeManager class.
+inVision keeps track of all nearby objects that the Zombunny can see for use in its pathfinding algorithm.
+the alignment is used for purposes of checking whether a Zombunny can damage other GameObjects, while visionCollider and damageCollider are the areas within which a Zombunny can see and deal damage from, respectively.
+The Rigidbody rigidBody handles physical collisions for movement purposes, while anim keeps track of the Zombunny's animation state, namely walking, idling, or death.
+
+\imfig{ZombieAgentInit}{The Genome, Awake, and Start methods of the ZombieAgent class}
+
+In Figure 14, Genome instantiates a
 

### 2018-12-09 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAgent.cs

@@ -35,7 +35,6 @@ namespace TowerDefense.Agents
         public readonly IAlignmentProvider alignment;
         public Collider visionCollider;
         public Collider damageCollider;
-        public Collider attackCollider;
         public Rigidbody rigidBody;
         public Animator anim;
 

### 2018-12-10 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAgent.cs
Add starvation mechanic

@@ -17,6 +17,7 @@ namespace TowerDefense.Agents
     {
         private readonly static float SINK_SPEED = 2.5f;
         private readonly static float SINK_TIME = 2.0f;
+        private readonly static float STARVATION_DISTANCE = 70.0f;
 
         public override Vector3 velocity
         {
@@ -44,6 +45,7 @@ namespace TowerDefense.Agents
         // For debug purposes only
         public float CurrentHealth = 0.1f;
         protected float damageDone = 0;
+        protected float distanceToStarve;
         
         // Increment total damage done over a zombie's lifetime
         public void addDamageDone(float increment)
@@ -74,6 +76,9 @@ namespace TowerDefense.Agents
         {
             base.Awake();
             configuration.died += OnDeath;
+            distanceToStarve = STARVATION_DISTANCE;
+            // Reset starvation on take damage
+            configuration.damaged += (_) => ResetStarvation();
         }
 
         /// <summary>
@@ -152,8 +157,17 @@ namespace TowerDefense.Agents
                 transform.position + 
                 (lastVelocity.toVector3() * Time.deltaTime));
 
+            // Starving
+            distanceToStarve -= lastVelocity.magnitude * Time.deltaTime;
+            if (distanceToStarve < 0) this.Kill();
+
             //For debug purposes only
             CurrentHealth = configuration.currentHealth;
+        }
+
+        public void ResetStarvation()
+        {
+            distanceToStarve = STARVATION_DISTANCE;
         }
 
         protected virtual void OnDeath(HealthChangeInfo _)

### 2018-12-10 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAttacker.cs

@@ -42,7 +42,10 @@ public class ZombieAttacker : MonoBehaviour {
                     zombieAgent.configuration.alignmentProvider
                 );
                 zombieAgent.addDamageDone(damage);
-                this.zombieAgent.addDamageDone(health - item.configuration.currentHealth);
+                if (damage > 0)
+                {
+                    zombieAgent.ResetStarvation();
+                }
             }
         }
     }

### 2018-12-10 TD/TowerDefense/Assets/Scripts/Evolution/Genome.cs
Softmax Working

@@ -12,9 +12,10 @@ namespace Evolution
         private readonly static float HEALTH_SCALE = 1;
         private readonly static float DAMAGE_SCALE = 1;
         private readonly static float MOVEMENT_SCALE = 0.4f;
-        
-        private static int current_id = 0;
 
+        private static ActivationSoftMax softMax;
+
+        private static int current_id = 0;
         private static int id_counter = 0;
 
         // ID # Makes sure that all genomes hash differently
@@ -27,26 +28,27 @@ namespace Evolution
             }
         }
 
-        // TODO: Use SoftMax for these distributions
-
-        private float health;
+        private float health_points;
+        private float health_scalar;
         public float Health {
             get {
-                return HEALTH_SCALE * (1 + health) * divisor;
+                return HEALTH_SCALE * health_scalar * totalStats;
             }
         }
 
-        private float damage;
+        private float damage_points;
+        private float damage_scalar;
         public float Damage {
             get {
-                return DAMAGE_SCALE * (1 + damage) * divisor;
+                return DAMAGE_SCALE * damage_scalar * totalStats;
             }
         }
 
-        private float movementSpeed;
+        private float speed_points;
+        private float speed_scalar;
         public float MovementSpeed {
             get {
-                return MOVEMENT_SCALE * (1 + movementSpeed) * divisor;
+                return MOVEMENT_SCALE * speed_scalar * totalStats;
             }
         }
 
@@ -59,10 +61,12 @@ namespace Evolution
             }
             set {
                 totalStats = value;
-                var NUM_STATS = 3;
-                var sum = movementSpeed + damage + health + NUM_STATS - Mathf.Min(movementSpeed, damage, health);
-                divisor = totalStats / (sum);
-                MonoBehaviour.print("Movement Speed: " + MovementSpeed);
+                double[] stat_array = new double[] { speed_points, damage_points, health_points };
+                softMax.ActivationFunction(stat_array, 0, stat_array.Length);
+                speed_scalar = (float)stat_array[0];
+                damage_scalar = (float)stat_array[1];
+                health_scalar = (float)stat_array[2];
+                MonoBehaviour.print($"Health: ({health_scalar}, {Health}), Damage: ({damage_scalar}, {Damage}), Speed: ({speed_scalar}, {MovementSpeed})");
             }
         }
 
@@ -72,9 +76,10 @@ namespace Evolution
 
         public Genome(float health, float damage, float movementSpeed, float totalStats)
         {
-            this.health = health;
-            this.damage = damage;
[…]

### 2018-12-10 paper.tex
paper progress

@@
 
-In Figure 14, Genome instantiates a
+In Figure 14, one can see the Genome, Awake, and Start methods of the ZombieAgent class.
+Genome instantiates a Zombunny's Genome object by pulling the var health from the given Genome, calling the SetMaxHealth and SetHealth methods, and setting the initial velocity vector to have an initial direction of $270^\circ$\----that is, in the general direction of the player's base relative to the spawn location, and magnitude determined by the MovementSpeed variable from the given Genome.
+Awake calls the underlying (base) Awake function and adds custom OnDeath behavior to a Zombunny.
+Start initializes the inVision HashSet of Targetable objects, which keeps track of nearby visible GameObjects.
+In the unexpected case that genome or lastVelocity are null, Start initializes these to default values (the "Zero" genome and a default velocity vector).
 

### 2018-12-10 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAgent.cs
Home base health working

@@ -17,7 +17,7 @@ namespace TowerDefense.Agents
     {
         private readonly static float SINK_SPEED = 2.5f;
         private readonly static float SINK_TIME = 2.0f;
-        private readonly static float STARVATION_DISTANCE = 70.0f;
+        private readonly static float STARVATION_DISTANCE = 40.0f;
 
         public override Vector3 velocity
         {

### 2018-12-10 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/PlayerHomeBase.cs

@@ -1,5 +1,6 @@
 ﻿using System.Collections.Generic;
 using ActionGameFramework.Audio;
+using ActionGameFramework.Health;
 using Core.Health;
 using TowerDefense.Agents;
 using UnityEngine;
@@ -9,130 +10,8 @@ namespace TowerDefense.Level
 	/// <summary>
 	/// A class representing the home base that players must defend
 	/// </summary>
-	public class PlayerHomeBase : DamageableBehaviour
+	public class PlayerHomeBase : Targetable
 	{
-		/// <summary>
-		/// The particle system when an attack is charging
-		/// </summary>
-		public ParticleSystem chargePfx;
-
-		/// <summary>
-		/// Sound to play when charge effect starts
-		/// </summary>
-		public RandomAudioSource chargeSound;
 		
-		/// <summary>
-		/// The particle system for an attack
-		/// </summary>
-		public ParticleSystem attackPfx;
-		
-		/// <summary>
-		/// Sound to play when attack effect starts
-		/// </summary>
-		public RandomAudioSource attackSound;
-
-		/// <summary>
-		/// The current Agents within the home base attack zone
-		/// </summary>
-		protected List<Agent> m_CurrentAgentsInside = new List<Agent>();
-
-		/// <summary>
-		/// Subscribes to damaged event
-		/// </summary>
-		protected virtual void Start()
-		{
-			configuration.damaged += OnDamaged;
-		}
-
-		/// <summary>
-		/// Unsubscribes to damaged event
-		/// </summary>
-		protected virtual void OnDestroy()
-		{
-			configuration.damaged -= OnDamaged;
-		}
-
-		/// <summary>
-		/// Plays <see cref="attackPfx"/> if assigned
-		/// </summary>
-		protected virtual void OnDamaged(HealthChangeInfo obj)
-		{
-			if (attackPfx != null)
-			{
-				attackPfx.Play();
-			}
-			if (attackSound != null)
-			{
-				attackSound.PlayRandomClip();
-			}
-		}
-		
-		/// <summary>
-		/// Adds triggered Agent to tracked Agents, subscribes to Agent's
-		/// removed event and plays pfx
-		/// </summary>
-		/// <param name="other">Triggered collider</param>
-		void OnTriggerEnter(Collider other)
-		{
[…]

### 2018-12-10 TD/TowerDefense/Assets/Scripts/TowerDefense/UI/HUD/PlayerBaseHealth.cs

@@ -1,4 +1,5 @@
-﻿using System.Globalization;
+﻿using System;
+using System.Globalization;
 using Core.Health;
 using TowerDefense.Level;
 using UnityEngine;
@@ -64,7 +65,7 @@ namespace TowerDefense.UI.HUD
 				return;
 			}
 			float currentHealth = levelManager.GetAllHomeBasesHealth();
-			display.text = currentHealth.ToString(CultureInfo.InvariantCulture);
-		}
+			display.text = Math.Round(currentHealth, 2).ToString(CultureInfo.InvariantCulture);
+		}   
 	}
 }

### 2018-12-10 paper.tex
More work on paper

@@
 
-In Figure 14, one can see the Genome, Awake, and Start methods of the ZombieAgent class.
-Genome instantiates a Zombunny's Genome object by pulling the var health from the given Genome, calling the SetMaxHealth and SetHealth methods, and setting the initial velocity vector to have an initial direction of $270^\circ$\----that is, in the general direction of the player's base relative to the spawn location, and magnitude determined by the MovementSpeed variable from the given Genome.
-Awake calls the underlying (base) Awake function and adds custom OnDeath behavior to a Zombunny.
-Start initializes the inVision HashSet of Targetable objects, which keeps track of nearby visible GameObjects.
-In the unexpected case that genome or lastVelocity are null, Start initializes these to default values (the "Zero" genome and a default velocity vector).
+In Figure 14, one can see the Genome, Awake, and Start methods of the
+ZombieAgent class. Genome instantiates a Zombunny's Genome object by pulling the
+var health from the given Genome, calling the SetMaxHealth and SetHealth
+methods, and setting the initial velocity vector to have an initial direction of
+$270^\circ$\----that is, in the general direction of the player's base relative
+to the spawn location, and magnitude determined by the MovementSpeed variable
+from the given Genome. Awake calls the underlying (base) Awake function and adds
+custom OnDeath behavior to a Zombunny. Start initializes the inVision HashSet of
+Targetable objects, which keeps track of nearby visible GameObjects. In the
+unexpected case that genome or lastVelocity are null, Start initializes these to
+default values (the "Zero" genome and a default velocity vector).
+
+\imfig{ZombieAgentVision}{The methods for keeping track of GameObjects entering
+  and exiting a Zombunny's visionCollider}
+
+Figure 15 shows the OnTriggerEnter and OnTriggerExit methods of the ZombieAgent
+class, which are used in conjunction with a Zombunny's visionCollider to update
+the inVision HashSet whenever a GameObject enters or exits the Zombunny's
+visionCollider radius.
+
+\imfig{ZombieAgentUpdateNearby}{The portions of the FixedUpdate method for
+determining the position of nearby objects relative to a Zombunny}
+
+Figure 16 shows the functions used to determine the position of GameObjects in
+inVision relative to a Zombunny's previous direction vector, stored as a
+dictionary of Targetables to PolarVectors. This allows a Zombunny to keep track
+of visible GameObjects relative to where it is currently facing.
+
+\imfig{ZombieAgentUpdateMovement}{The function of FixedUpdate for handling
+  movement between ticks}
+
+Figure 17 shows the portion of FixedUpdate dedicated to rotating a Zombunny from
+tick to tick, calling the Rotate method of the lastVelocity PolarVector using
+the CalculateDirection method of the genome class, taking into account the
+Zombunny's previous velocity vector, the time alive, the Zombunny's current
+health, and the aforementioned dictionary of nearby GameObjects.
+
+\imfig{ZombieAgentUpdateDeath}{The portion of FixedUpdate that handles
+  death/deletion}
+
+Figure 18 shows the part of the FixedUpdate method which keeps track of Zombunny
+death, destroying the Zombunny GameObject at the appropriate time and calling
+the relevant death animations. For every tick that a Zombunny is not dead,
+FixedUpdate will increment timeAlive, which is later used as a factor in
+calculating fitness.
+
+\subsubsection{ZombieAttacker}
+
+The ZombieAttacker class calls Update on each tick, dealing damage to any item
+in toAttack, which is a HashSet of Targetable GameObjects that intersect with
+a Zombunny's attack collider (see Figure 4). This way, a Zombunny can attack
+multiple GameObjects so long as they intersect with its attack collider. Damage
+is applied to items in toAttack by calling their individual takeDamage methods,
+with the damage dealt as determined by the Zombunny's genome passed as a
+parameter.
+
+\imfig{}{}
 

### 2018-12-10 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/GenomeManager.cs
Work towards reproduction

@@ -4,6 +4,7 @@ using UnityEngine;
 using Evolution;
 using TowerDefense.Agents;
 using Redzen.Numerics.Distributions.Float;
+using Util;
 
 namespace TowerDefense.Level
 {
@@ -11,20 +12,20 @@ namespace TowerDefense.Level
         /// <summary>
         /// How many zombunnies to spawn
         /// </summary>
-        public readonly int POPULATION_SIZE = 10;
+        public static readonly int POPULATION_SIZE = 10;
 
         /// <summary>
         /// The mutation rate
         /// </summary>
-        public readonly float MUTATION_RATE = 0.2f;
+        public static readonly float MUTATION_RATE = 0.2f;
 
-        public readonly float GROWTH_RATE = 0.3f;
+        public static readonly float GROWTH_RATE = 0.3f;
 
-        public readonly float SPAWN_DELAY = 2f;
+        public static readonly float SPAWN_DELAY = 2f;
 
-        private readonly static float STARTING_TOTAL = 16f;
+        private static readonly float STARTING_TOTAL = 16f;
 
-        private readonly static double INITIAL_FITNESS = 0.0;
+        private static readonly double INITIAL_FITNESS = 0.0;
 
         /// <summary>
         /// The prefab to spawn as an enemy
@@ -68,7 +69,13 @@ namespace TowerDefense.Level
         private void NextWave()
         {
             var nextWave = new Stack<Genome>(POPULATION_SIZE);
+
+            //Cull wave
+            var culled = Cull(currentMap);
+            
             // Reproduce Here! dict -> list
+            
+
             foreach (var pair in currentMap)
             {
                 if (pair.Key == null) continue;
@@ -103,6 +110,48 @@ namespace TowerDefense.Level
             {
                 ZombieDied(agentInstance);
             };
+        }
+
+        private static List<Pair<double, Genome>> Cull(Dictionary<Genome, double> toCull)
+        {
+            double max_fitness = 0;
+            foreach (var fitness in toCull.Values)
+            {
+                if (fitness > max_fitness)
+                {
+                    max_fitness = fitness;
+                }
+            }
+            var ret = new List<Pair<double, Genome>>(toCull.Count);
+            foreach (var pair in toCull)
+            {
+                var chance = pair.Value / max_fitness;
+                if (Random.value < chance)
+                {
+                    ret.Add(new Pair<double, Genome>(pair.Value, pair.Key));
+                }
+            }
+            return ret;
+        }
+
[…]

### 2018-12-10 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/Pair.cs

@@ -1,0 +1,6 @@
+﻿namespace TowerDefense.Level
+{
+    internal class Pair<T1, T2>
+    {
+    }
+}

### 2018-12-10 TD/TowerDefense/Assets/Scripts/Util/Pair.cs

@@ -1,0 +1,13 @@
+﻿namespace Util
+{
+    internal class Pair<T1, T2>
+    {
+        public T1 First;
+        public T2 Second;
+        public Pair(T1 First, T2 Second)
+        {
+            this.First = First;
+            this.Second = Second;
+        }
+    }
+}

### 2018-12-10 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/GenomeManager.cs
Work on reproduction

@@ -147,11 +147,35 @@ namespace TowerDefense.Level
             {
                 double rand = Random.value * sum_fitness;
                 double last_pos = 0;
-                for(int jj = 0; jj < toReproduce.Count; ++jj)
+                int jj;
+                for(jj = 0; jj < toReproduce.Count; ++jj)
                 {
-
+                    last_pos += toReproduce[jj].First;
+                    if (rand < last_pos) break;
                 }
+                unshuffled.Add(toReproduce[jj].Second);
             }
+            foreach (var pair in toReproduce)
+            {
+                unshuffled.Add(pair.Second);
+            }
+            // Shuffle genome
+            return new Stack<Genome>(unshuffled);
+        }
+
+        private static List<Genome> Shuffle(List<Genome> genomes)
+        {
+            //FIXME
+            int n = genomes.Count;
+            while (n > 1)
+            {
+                n--;
+                int k = Random.Range(0, 1);
+                Genome value = genomes[k];
+                genomes[k] = genomes[n];
+                genomes[n] = value;
+            }
+            return genomes;
         }
 
         //Callback function on zombunny death

### 2018-12-10 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/Pair.cs

@@ -1,6 +1,0 @@
-﻿namespace TowerDefense.Level
-{
-    internal class Pair<T1, T2>
-    {
-    }
-}

### 2018-12-11 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/GenomeManager.cs
Shuffle working

@@ -160,22 +160,29 @@ namespace TowerDefense.Level
                 unshuffled.Add(pair.Second);
             }
             // Shuffle genome
-            return new Stack<Genome>(unshuffled);
+            return Shuffle(unshuffled);
         }
 
-        private static List<Genome> Shuffle(List<Genome> genomes)
+        /// <summary>
+        /// Simple Fisher-Yates Shuffle
+        /// WARNING: CONSUMES INPUT
+        /// </summary>
+        /// <param name="genomes"></param>
+        /// <returns></returns>
+        private static Stack<Genome> Shuffle(List<Genome> genomes)
         {
-            //FIXME
+            var ret = new Stack<Genome>(genomes.Count);
             int n = genomes.Count;
             while (n > 1)
             {
                 n--;
-                int k = Random.Range(0, 1);
+                int k = Random.Range(0, n);
                 Genome value = genomes[k];
                 genomes[k] = genomes[n];
                 genomes[n] = value;
+                ret.Push(value);
             }
-            return genomes;
+            return ret;
         }
 
         //Callback function on zombunny death

### 2018-12-11 paper.tex

@@
 \imfig{BaseExample}{An example set of player defenses around the home base}
-In \tavs, the player must defend their home base against the aforementioned onslaught of enemies such as the fearsome Zombunny (see Figure 3).
-Zombunnies are driven by a single goal: destruction of the player's home base.
-Zombunnies spawn in groups of ten (separated by a slight delay) at the beginning of the game.
-Subsequent waves spawn after all members from the previous wave have died.
-Zombunnies use a genetic algorithm in conjunction with a recurrent neural network to evolve a pathfinding algorithm between generations (waves), with the long-term incentive of dealing damage to the player's base (explain fitness criteria more concisely here).
-Zombunnies can be killed by either taking damage from a player's defenses or through "starvation." A Zombunny will starve to death if it does not take or deal damage for a given length of time.
-Through this starvation mechanism, the Zombunnies which survive the longest are ultimately those which interact the most with the player's defenses, and are subsequently more likely to pass on attributes of their genome to the next generation.
-Zombunnies have three characteristic attributes: health, damage, and movement speed.
-All three of these stats are assigned upon spawning as dictated by their genome.
-Pathfinding is controlled by a recurrent neural net, whose weights are determined through a genetic algorithm between waves, which optimizes for Zombunnies' ability to achieve their overarching goal of player base destruction.
-Zombunnies can "see" nearby entities within a certain radius, including other Zombunnies, player defenses, and the player's home base (when in range).
-Based on the combination of visible inputs, Zombunnies will output a chosen direction which they will then walk in.
-This algorithm updates on a tick-by-tick basis.
-Zombunnies will damage structures they collide with.
-Because evolution of the pathfinding neural net only happens between generations, near the beginning of the game, Zombunnies will start off with relatively stupid pathfinding which will typically cause the first few populations to starve to death without dealing any significant damage.
-This provides the player with an initial grace period during which they may build their initial defenses.
-As time goes on, Zombunnies will evolve towards an optimal stat distribution of health, damage, and speed, as well as in their ability to pathfind in such a way as to thwart the player's defenses and end the game.
+In \tavs, the player must defend their home base against the aforementioned
+onslaught of enemies such as the fearsome Zombunny (see Figure 3). Zombunnies
+are driven by a single goal: destruction of the player's home base. Zombunnies
+spawn in groups of ten (separated by a slight delay) at the beginning of the
+game. Subsequent waves spawn after all members from the previous wave have died.
+Zombunnies use a genetic algorithm in conjunction with a recurrent neural
+network to evolve a pathfinding algorithm between generations (waves), with the
+long-term incentive of dealing damage to the player's base% (explain fitness
+% criteria more concisely here)
+. Zombunnies can be killed by either taking damage
+from a player's defenses or through "starvation." A Zombunny will starve to
+death if it does not take or deal damage for a given length of time. Through
+this starvation mechanism, the Zombunnies which survive the longest are
+ultimately those which interact the most with the player's defenses, and are
+subsequently more likely to pass on attributes of their genome to the next
+generation. Zombunnies have three characteristic attributes: health, damage, and
+movement speed. All three of these stats are assigned upon spawning as dictated
+by their genome. Pathfinding is controlled by a recurrent neural net, whose
+weights are determined through a genetic algorithm between waves, which
+optimizes for Zombunnies' ability to achieve their overarching goal of player
+base destruction. Zombunnies can "see" nearby entities within a certain radius,
+including other Zombunnies, player defenses, and the player's home base (when in
+range). Based on the combination of visible inputs, Zombunnies will output a
+chosen direction which they will then walk in. This algorithm updates on a
+tick-by-tick basis. Zombunnies will damage structures they collide with. Because
+evolution of the pathfinding neural net only happens between generations, near
+the beginning of the game, Zombunnies will start off with relatively stupid
+pathfinding which will typically cause the first few populations to starve to
+death without dealing any significant damage. This provides the player with an
+initial grace period during which they may build their initial defenses. As time
+goes on, Zombunnies will evolve towards an optimal stat distribution of health,
+damage, and speed, as well as in their ability to pathfind in such a way as to
+thwart the player's defenses and end the game.
 
@@
 the relevant death animations. For every tick that a Zombunny is not dead,
-FixedUpdate will increment timeAlive, which is later used as a factor in
+FixedUpdate increments timeAlive, which is later used as a factor in
 calculating fitness.
@@
 
-The ZombieAttacker class calls Update on each tick, dealing damage to any item
+The ZombieAttacker class (see Figure 19) calls Update on each tick, dealing damage to any item
 in toAttack, which is a HashSet of Targetable GameObjects that intersect with
@@
 
-\imfig{}{}
+\imfig{ZombieAttacker}{The Update method of the ZombieAttacker class}
 

### 2018-12-11 paper.tex
More work on paper

@@
 In \tavs, the player must defend their home base against the aforementioned
-onslaught of enemies such as the fearsome Zombunny (see Figure 3). Zombunnies
+onslaught of enemies such as the fearsome Zombunny (see Figure 4). Zombunnies
 are driven by a single goal: destruction of the player's home base. Zombunnies
@@
 
-Insert picture of \textit{They Are Billions} gameplay here.
+%Insert picture of \textit{They Are Billions} gameplay here.%
 
@@
 
-The Spawn method, as seen in Figure 12, is called every SPAWN\_DELAY interval POPULATION\_COUNT times.
+The Spawn method, as seen in Figure 12, is called at every SPAWN\_DELAY interval POPULATION\_COUNT times.
 The function starts by spawning a Zombunny with no genome due to the inability to provide parameters upon GameObject instantiation.
@@
 Thus, we had to manually delete most of the library files and remove underscore digit separators from some numeric constants, as they are a C\# 7 feature.
-You can find our compatible library at \path{They-Are-Very-Smart/TD/TowerDefense/Assets/Scripts/Util/Redzen}
+You can find our compatible library at \path{They-Are-Very-Smart/TD/TowerDefense/Assets/Scripts/Util/Redzen}.
 
@@
 setting health, damage, and speed as determined by the genome, as well as handling tick-to-tick operations during a Zombunny's lifetime.
-These tick-to-tick operations include choosing the next movement vector based on the location of nearby GameObjects and agent's current status.
+These tick-to-tick operations include choosing the next movement vector based on the location of nearby GameObjects and agents' current status.
 
-\imfig{ZombieAgent1}{ZombieAgent class parameters}
+\imfigH{ZombieAgent1}{ZombieAgent class parameters}
 
@@
 
-\imfig{ZombieAgentVision}{The methods for keeping track of GameObjects entering
+\imfigH{ZombieAgentVision}{Methods for keeping track of GameObjects entering
   and exiting a Zombunny's visionCollider}
@@
 
-\imfig{ZombieAgentUpdateNearby}{The portions of the FixedUpdate method for
+\imfigB{ZombieAgentUpdateNearby}{The portion of the FixedUpdate method for
 determining the position of nearby objects relative to a Zombunny}
@@
 
-Figure 17 shows the portion of FixedUpdate dedicated to rotating a Zombunny from
-tick to tick, calling the Rotate method of the lastVelocity PolarVector using
-the CalculateDirection method of the genome class, taking into account the
-Zombunny's previous velocity vector, the time alive, the Zombunny's current
-health, and the aforementioned dictionary of nearby GameObjects.
+Figure 17 shows the portion of FixedUpdate dedicated to altering a Zombunny's
+trajectory from tick to tick, calling the Rotate method of the lastVelocity
+PolarVector using the CalculateDirection method of the genome class, taking into
+account the Zombunny's previous velocity vector, time alive, current health, and
+the aforementioned dictionary of nearby GameObjects.
 
@@
 \imfig{ZombieAttacker}{The Update method of the ZombieAttacker class}
+
+\subsection{Evolution}
+
+In \
 

### 2018-12-11 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/GenomeManager.cs
Working start button

@@ -45,8 +45,8 @@ namespace TowerDefense.Level
         private Stack<Genome> toSpawn;
         private ZombieAgent prefabAgent;
         private ZigguratGaussianSampler sampler;
-
-        private void Start()
+            
+        public void StartSpawning()
         {
             GenerateInitialGenomes();
             NextWave();

### 2018-12-11 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/LevelManager.cs

@@ -11,7 +11,7 @@ namespace TowerDefense.Level
 	/// <summary>
 	/// The level manager - handles the level states and tracks the player's currency
 	/// </summary>
-	[RequireComponent(typeof(WaveManager))]
+	[RequireComponent(typeof(GenomeManager)),RequireComponent(typeof(WaveManager))]
 	public class LevelManager : Singleton<LevelManager>
 	{
 		/// <summary>
@@ -51,6 +51,11 @@ namespace TowerDefense.Level
 		/// The attached wave manager
 		/// </summary>
 		public WaveManager waveManager { get; protected set; }
+
+        /// <summary>
+        /// Genome manager
+        /// </summary>
+        public GenomeManager genomeManager;
 
 		/// <summary>
 		/// Number of enemies currently in the level
@@ -276,7 +281,7 @@ namespace TowerDefense.Level
 			switch (newState)
 			{
 				case LevelState.SpawningEnemies:
-					waveManager.StartWaves();
+                    genomeManager.StartSpawning();
 					break;
 				case LevelState.AllEnemiesSpawned:
 					// Win immediately if all enemies are already dead

### 2018-12-11 TD/TowerDefense/Assets/Scripts/Evolution/PolarVector.cs
Fixed vector math

@@ -47,7 +47,9 @@ namespace Evolution
         public static PolarVector fromVector3(Vector3 vv)
         {
             Vector3 withoutY = new Vector3(vv.x, 0, vv.z);
-            return new PolarVector(withoutY.magnitude, Vector3.Angle(E1, withoutY));
+            var angle = Vector3.Angle(E1, withoutY);
+            if (withoutY.z < 0) angle = -angle;
+            return new PolarVector(angle, withoutY.magnitude);
         }
 
         public Vector3 toVector3()
@@ -62,6 +64,11 @@ namespace Evolution
         public static Vector3 toVector3(PolarVector vv)
         {
             return vv.toVector3();
+        }
+
+        public override string ToString()
+        {
+            return $"({this.direction} deg, {magnitude})";
         }
     }
 }

### 2018-12-11 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAgent.cs

@@ -62,12 +62,6 @@ namespace TowerDefense.Agents
             }
             set
             {
-                lastVelocity = new PolarVector(270);
-                genome = value;
-                var health = genome.Health;
-                configuration.SetMaxHealth(health);
-                configuration.SetHealth(health);
-                lastVelocity.magnitude = genome.MovementSpeed;
                 genome = value;
             }
         }
@@ -91,6 +85,20 @@ namespace TowerDefense.Agents
             {
                 this.lastVelocity = new PolarVector(0, 1f);
             }
+        }
+
+        public void Initialize(Genome genome, Vector3 target, Vector3 spawnPostition)
+        {
+            target.y = 0;
+            spawnPostition.y = 0;
+            var difference = target - spawnPostition;
+            print($"Target: {target}, Spawn: {spawnPostition}, Difference: {difference}");
+            lastVelocity = PolarVector.fromVector3(difference);
+            this.genome = genome;
+            var health = genome.Health;
+            configuration.SetMaxHealth(health);
+            configuration.SetHealth(health);
+            lastVelocity.magnitude = genome.MovementSpeed;
         }
 
         private void OnTriggerEnter(Collider other)

### 2018-12-11 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/GenomeManager.cs

@@ -8,6 +8,7 @@ using Util;
 
 namespace TowerDefense.Level
 {
+    [RequireComponent(typeof(PlayerHomeBase))]
     public class GenomeManager : MonoBehaviour {
         /// <summary>
         /// How many zombunnies to spawn
@@ -37,15 +38,21 @@ namespace TowerDefense.Level
         /// </summary>
         public List<Transform> SpawnPoints;
 
+        /// <summary>
+        /// Where the zombies start facing
+        /// </summary>
+        public PlayerHomeBase target;
+
         private int remaining_alive;
         private List<Dictionary<Genome, double>> genomeMaps;
         private Dictionary<Genome, double> currentMap;
+
 
         // TODO
         private Stack<Genome> toSpawn;
         private ZombieAgent prefabAgent;
         private ZigguratGaussianSampler sampler;
-            
+        
         public void StartSpawning()
         {
             GenerateInitialGenomes();
@@ -102,10 +109,9 @@ namespace TowerDefense.Level
                 CancelInvoke("Spawn");
             }
             int spawn_index = Random.Range(0, SpawnPoints.Count);
-
             var prefabInstance = Instantiate(ZombiePrefab, SpawnPoints[spawn_index]);
             var agentInstance = prefabInstance.GetComponent<ZombieAgent>();
-            agentInstance.Genome = toSpawn.Pop();
+            agentInstance.Initialize(toSpawn.Pop(), target.position, SpawnPoints[spawn_index].position);
             agentInstance.removed += (_) =>
             {
                 ZombieDied(agentInstance);

### 2018-12-11 TD/TowerDefense/Assets/Scripts/Core/Health/DamageableBehaviour.cs
Fixed starvation

@@ -52,16 +52,16 @@ namespace Core.Health
 		/// <param name="damageValue">Damage value.</param>
 		/// <param name="damagePoint">Damage point.</param>
 		/// <param name="alignment">Alignment value</param>
-		public virtual float TakeDamage(float damageValue, Vector3 damagePoint, IAlignmentProvider alignment)
+		public virtual bool TakeDamage(float damageValue, Vector3 damagePoint, IAlignmentProvider alignment)
 		{
 			HealthChangeInfo info;
-			configuration.TakeDamage(damageValue, alignment, out info);
+			var ret = configuration.TakeDamage(damageValue, alignment, out info);
 			var damageInfo = new HitInfo(info, damagePoint);
 			if (hit != null)
 			{
 				hit(damageInfo);
 			}
-            return damageInfo.healthChangeInfo.absHealthDifference;
+            return ret;
 		}
 
 		protected virtual void Awake()

### 2018-12-11 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAttacker.cs

@@ -36,14 +36,14 @@ public class ZombieAttacker : MonoBehaviour {
             if (item != null)
             {
                 float health = item.configuration.currentHealth;
-                float damage = item.TakeDamage(
-                    zombieAgent.Genome.Damage * Time.deltaTime,
+                float damage_to_do = zombieAgent.Genome.Damage * Time.deltaTime;
+                if (item.TakeDamage(
+                    damage_to_do,
                     zombieAgent.transform.position,
                     zombieAgent.configuration.alignmentProvider
-                );
-                zombieAgent.addDamageDone(damage);
-                if (damage > 0)
+                ))
                 {
+                    zombieAgent.addDamageDone(damage_to_do);
                     zombieAgent.ResetStarvation();
                 }
             }

### 2018-12-11 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/GenomeManager.cs

@@ -111,7 +111,7 @@ namespace TowerDefense.Level
             int spawn_index = Random.Range(0, SpawnPoints.Count);
             var prefabInstance = Instantiate(ZombiePrefab, SpawnPoints[spawn_index]);
             var agentInstance = prefabInstance.GetComponent<ZombieAgent>();
-            agentInstance.Initialize(toSpawn.Pop(), target.position, SpawnPoints[spawn_index].position);
+            agentInstance.Initialize(toSpawn.Pop(), target.transform.position, SpawnPoints[spawn_index].position);
             agentInstance.removed += (_) =>
             {
                 ZombieDied(agentInstance);

### 2018-12-11 TD/TowerDefense/Assets/Scripts/Evolution/Genome.cs
absolute walk towards working

@@ -4,6 +4,7 @@ using System.Collections.Generic;
 using ActionGameFramework.Health;
 using Redzen.Numerics.Distributions.Float;
 using Encog.Engine.Network.Activation;
+using TowerDefense.Level;
 
 namespace Evolution
 {
@@ -104,6 +105,7 @@ namespace Evolution
                 );
         }
 
+
         /// <summary>
         /// Calcualtes the direction that the genome would have the zombie move
         /// </summary>
@@ -114,13 +116,35 @@ namespace Evolution
         /// <param name="nearby">dictionary from nearby entities mapped to the vector to them</param>
         /// <returns>direction, The direction to move in</returns>
         public float CalculateDirection(
-            PolarVector previous_direction, 
+            PolarVector previous_direction,
             int time_alive,
             float health,
             Dictionary<Targetable, PolarVector> nearby
             )
         {
-            return 0f;
+            KeyValuePair<Targetable, PolarVector> target;
+            bool seen = false;
+            var count = 0;
+            foreach (var pair in nearby)
+            {
+                if (pair.Key.GetType() == typeof(PlayerHomeBase)) ++count;
+            }
+
+            foreach (var pair in nearby)
+            {
+                var targetableType = pair.Key.GetType();
+                if (targetableType == typeof(PlayerHomeBase))
+                {
+                    target = pair;
+                    seen = true;
+                    break;
+                }
+            }
+            if (seen)
+            {
+                return target.Value.direction;// - previous_direction.direction;
+            }
+            return previous_direction.direction;
         }
     }
 }

### 2018-12-11 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAgent.cs

@@ -142,23 +142,27 @@ namespace TowerDefense.Agents
             foreach(var item in inVision)
             {
                 if (item == null) continue;
-                nearbyDict.Add(
-                    item,
-                    new PolarVector(
-                            (- lastVelocity.direction) + Vector3.Angle(transform.position, item.gameObject.transform.position),
-                            Vector3.Distance(transform.position, item.gameObject.transform.position)
-                        )
-                 );
+                Vector3 zomPos = transform.position;
+                Vector3 targetPos = item.gameObject.transform.position;
+                Vector3 zomToTarget = targetPos - zomPos;
+                PolarVector zomToTargetP = PolarVector.fromVector3(zomToTarget);
+                //zomToTargetP.direction -= lastVelocity.direction;
+                nearbyDict.Add(item, zomToTargetP);
             }
 
 
             // Handle Movement
-            lastVelocity.Rotate(
-                genome.CalculateDirection(
-                lastVelocity, 
-                time_alive, 
-                configuration.currentHealth, 
-                nearbyDict));
+            //lastVelocity.Rotate(
+            //    genome.CalculateDirection(
+            //    lastVelocity, 
+            //    time_alive, 
+            //    configuration.currentHealth, 
+            //    nearbyDict));
+            lastVelocity.direction = genome.CalculateDirection(
+                lastVelocity,
+                time_alive,
+                configuration.currentHealth,
+                nearbyDict);
 
             rigidBody.MoveRotation(Quaternion.LookRotation(lastVelocity.toVector3()));
             rigidBody.MovePosition(

### 2018-12-11 paper.tex
More paper tweaks

@@
 
+%figure 5%
 \imfigB{PolarVector1}{The basics of PolarVector}
@@
 
-The mutation function in Figure 8 essentially creates a new copy of the current genome, nudged by normally distributed random numbers.
+The mutation function in Figure 8 essentially creates a new copy of the current genome, which is then nudged by normally distributed random numbers.
 
@@
 
-\imfigB{ZombieAgentUpdateNearby}{The portion of the FixedUpdate method for
+\imfigH{ZombieAgentUpdateNearby}{The portion of the FixedUpdate method for
 determining the position of nearby objects relative to a Zombunny}
@@
 
-\imfig{ZombieAgentUpdateMovement}{The function of FixedUpdate for handling
+\imfig{ZombieAgentUpdateMovement}{The function of FixedUpdate that handles
   movement between ticks}
@@
 multiple GameObjects so long as they intersect with its attack collider. Damage
-is applied to items in toAttack by calling their individual takeDamage methods,
-with the damage dealt as determined by the Zombunny's genome passed as a
-parameter.
+is applied to items in toAttack by calling their individual takeDamage methods.
+Damage dealt is determined by the Zombunny's genome, and is passed as a parameter 
+to takeDamage.
 
@@
 
-\subsection{Evolution}
+\subsection{Genetic Algorithm}
 
-In \
+In \tavs,
 
@@
 At this time, we are waiting on actual results from our project.
-We hope that given a large enough population of zombies, we might see
-populations of zombies evolving to counteract players' strategies. Evolution
+We hope that given a large enough population of Zombunnies, we might see
+populations of Zombunnies evolving to counteract players' strategies. Evolution
 will likely have little trouble tackling a trivial or consistent player
@@
 Sexual (genderless) reproduction could also be introduced as a way of trying to
-increase diversity. Plain sexual reproduction without any further restrictions
+incentivize diversity. Plain sexual reproduction without any further restrictions
 could allow good traits that evolve in parallel to be combined into a single
@@
 fitness, and then run them through a tournament to determine mates. This would
-have the additional benefit of allowing additional emergent behavior that has
-not been conceived of in this speculation.
+have the additional benefit of allowing emergent behavior that has not been 
+conceived of in this speculation.
 

### 2018-12-12 paper.tex
Paper: Intro edits

@@
 network to evolve a pathfinding algorithm between generations (waves), with the
-long-term incentive of dealing damage to the player's base% (explain fitness
-% criteria more concisely here)
-. Zombunnies can be killed by either taking damage
-from a player's defenses or through "starvation." A Zombunny will starve to
-death if it does not take or deal damage for a given length of time. Through
-this starvation mechanism, the Zombunnies which survive the longest are
-ultimately those which interact the most with the player's defenses, and are
-subsequently more likely to pass on attributes of their genome to the next
-generation. Zombunnies have three characteristic attributes: health, damage, and
-movement speed. All three of these stats are assigned upon spawning as dictated
-by their genome. Pathfinding is controlled by a recurrent neural net, whose
-weights are determined through a genetic algorithm between waves, which
-optimizes for Zombunnies' ability to achieve their overarching goal of player
-base destruction. Zombunnies can "see" nearby entities within a certain radius,
-including other Zombunnies, player defenses, and the player's home base (when in
-range). Based on the combination of visible inputs, Zombunnies will output a
-chosen direction which they will then walk in. This algorithm updates on a
-tick-by-tick basis. Zombunnies will damage structures they collide with. Because
-evolution of the pathfinding neural net only happens between generations, near
-the beginning of the game, Zombunnies will start off with relatively stupid
-pathfinding which will typically cause the first few populations to starve to
-death without dealing any significant damage. This provides the player with an
-initial grace period during which they may build their initial defenses. As time
-goes on, Zombunnies will evolve towards an optimal stat distribution of health,
-damage, and speed, as well as in their ability to pathfind in such a way as to
-thwart the player's defenses and end the game.
+ultimate goal of dealing damage to (and therefore destroying) the player's base
+. Zombunnies can be killed by either taking damage from a player's defenses or
+through "starvation." A Zombunny will starve to death if it does not take or
+deal damage for a set moved distance. Through this starvation mechanism, the
+Zombunnies which survive the longest are ultimately those which interact the
+most with the player's defenses. Zombunnies have three
+characteristic attributes: health, damage, and movement speed. All three of
+these stats are assigned upon spawning as dictated by their genome. Pathfinding
+is controlled by a recurrent neural net, whose topology and weight is encoded in
+the genome alongside of the characteristic attributes. The neural net evolves on
+a wave by wave basis, with those genomes that preform better being more likely
+to survive and reproduce than their peers, optimizing for Zombunnies' ability to
+achieve their overarching goal of player base destruction. Zombunnies can "see"
+nearby entities within a certain radius, including other Zombunnies, player
+defenses, and the player's home base (when in range). Based on the combination
+of visible inputs, Zombunnies will output a chosen direction which they will
+then walk in. This algorithm updates on a tick-by-tick basis. Zombunnies will
+damage structures they collide with. Because evolution of the pathfinding neural
+net only happens between generations, near the beginning of the game, Zombunnies
+will start off with relatively stupid pathfinding which will typically cause the
+first few populations to starve to death without dealing any significant damage.
+This provides the player with an initial grace period during which they may
+build their initial defenses. As time goes on, Zombunnies will evolve towards an
+optimal stat distributions of health, damage, and speed, as well as in their
+ability to pathfind in such a way as to thwart the player's defenses and end the
+game.
 
@@
 
-\tavs~was initially inspired by Numantian Games' \textit{They Are Billions}, a game in which a player must build defenses in order to fend off a zombie apocalypse.
-The game features massive numbers of zombies.
-This project emerged from an interest in what \textit{They Are Billions} would be like if the zombies could actually think for themselves.
-The result is significantly pared down in comparison, as the focus has been on zombie evolution as opposed to player interactivity and enjoyability.
-However, similarities to \textit{They Are Billions} can be seen in the resource management system, the player's defense of a citadel, and need to fend off the faceless hordes.
-In contrast, \textit{They Are Billions} puts additional emphasis on world generation, player exploration, and narrative elements.
+\tavs~was initially inspired by Numantian Games' \textit{They Are Billions}, a
+game in which a player must build defenses in order to fend off a zombie
+apocalypse. The game features massive numbers of zombies. This project emerged
+from an interest in what \textit{They Are Billions} would be like if the zombies
+could learn and evolve similarly to a real virus. The result is significantly pared down in
+comparison, as the focus has been on zombie evolution as opposed to player
+interactivity and enjoyment. However, similarities to \textit{They Are
+  Billions} can be seen in the resource management system, the player's defense
+of a citadel, and need to fend off the faceless hordes. In contrast,
+\textit{They Are Billions} puts additional emphasis on world generation, player
+exploration, and narrative elements.
 

### 2018-12-12 paper.tex
Paper: git issues
Made Zombunnies smaller, added spawn points, and increased spawn rate and population size.

@@
 Players, on the other hand, may also learn to optimize around our implementation
-of evolution. Conceivably clever player could develop two very different
+of evolution. Conceivably clever players could develop two very different
 strategies ahead of time. The player would first implement the weaker strategy,
@@
 back-propagate the reward/fitness function to learn, which opens up the
-possibility to drop in a nerual net to replace any function in a learning
+possibility to drop in a neural net to replace any function in a learning
 environment; on a larger timescale, the selection tournament process itself

### 2018-12-12 paper.tex
Paper: add hyperparameters section

--- 2018-12-12 paper.tex
@@
 \section{Background}
-In \tavs, we utilize a basic genetic algorithm to train a recurrent neural network generated using the Neuroevolution of Augmenting Topologies (NEAT) method and \href{https://www.heatonresearch.com/encog/}{Encog} framework, which can be found \href{https://sharpneat.sourceforge.net/}{here}, which is a generalized deep-learning library that includes implementations of NEAT and HyperNEAT.
+In \tavs, we utilize a basic genetic algorithm to train a recurrent neural
+network generated using the Neuroevolution of Augmenting Topologies (NEAT)
+method (implemented in the \href{https://www.heatonresearch.com/encog/}{Encog}
+framework), which can be found \href{https://sharpneat.sourceforge.net/}{here},
+which is a generalized deep-learning library that includes implementations of
+a large number of NEAT and HyperNEAT.
 
@@
 \subsection{Code overview}
+\subsubsection{Hyperparameters}
+The hyperparameters relevant to playing with how the games are the constants at
+the top of \path{Assets/Scripts/Evolution/Genome.cs}, \texttt{HEALTH_SCALE},
+\texttt{DAMAGE_SCALE}, and \texttt{MOVEMENT_SCALE}; and at the top of
+\path{Assets/Scripts/TowerDefence/Level/GenomeManager.cs}, with
+\texttt{POPULATION_SIZE}, \texttt{MUTATION_RATE}, \texttt{GROWTH_RATE},
+\texttt{SPAWN_DELAY}, and \texttt{STARTING_TOTAL}. The scale constants in
+\path{Genome.cs} change how health, speed, and damage are scaled relative to
+each other. \texttt{POPULATION_SIZE} represents the number of genomes (and
+therefore zombunnies) in every generation. \texttt{MUTATION_RATE} determines how
+much variance there is in everey mutation operation. \texttt{GROWTH_RATE}
+Determines how much combined speed, health, and damage is available to be
+distributed. \texttt{SPAWN_DELAY} determines how much time passes between spawns
+in waves. \texttt{STARTING_TOTAL} determines the total number of stats available
+to the zombunnies at the start of the game.
+
 \subsubsection{PolarVector}

### 2018-12-12 paper.tex
Paper: polarvector edits

@@
 
-The implementation details of PolarVector's conversion functions are fairly trivially derived from math, but it should be noted that all Cartesian components are encoded as Vector3 components as the game takes place on the X-Z plane (see Figure 6).
+The implementation details of PolarVector's conversion functions are fairly
+trivially derived from math, but it should be noted that all Cartesian
+components are encoded as two dimensions of a \texttt{Vector3} as the game takes
+place on the X-Z plane (see Figure 6).
 

### 2018-12-12 paper.tex
Paper: genome edits

@@
 \subsubsection{Genome}
-The Genome class encapsulates the data that is stored on a genome-by-genome basis, and provides most of the procedures that deal with their mutation, as well as providing conversions from their internal state to the game-useful health, speed, and damage values, as well as providing an interface to conveniently call the resulting pathfinding neural net.
+The Genome class encapsulates the data that is stored on a genome-by-genome
+basis, provides most of the procedures that deal with their mutation, provides
+conversions from their internal state to the game-useful health, speed, and
+damage values, and provides an interface to conveniently call the resulting
+pathfinding neural net.
 
@@
 
-In Figure 7, we can see the constants that are used to scale a Zombunny's health, movement speed, and damage, which need to be set manually.
-The Id field is used as a unique identifier if genomes need to be looked up, and also ensures that every genome will hash differently.
+In Figure 7, we can see the constants that are used to scale a Zombunny's
+health, movement speed, and damage, which need to be set manually as discussed
+in the hyperparameters sections. The Id field is used as a unique identifier if
+genomes need to be looked up, and also ensures that every genome will hash differently.
 

### 2018-12-12 paper.tex
Things are evolving

@@
 The hyperparameters relevant to playing with how the games are the constants at
-the top of \path{Assets/Scripts/Evolution/Genome.cs}, \texttt{HEALTH_SCALE},
-\texttt{DAMAGE_SCALE}, and \texttt{MOVEMENT_SCALE}; and at the top of
+the top of \path{Assets/Scripts/Evolution/Genome.cs}, \texttt{HEALTH\_SCALE},
+\texttt{DAMAGE\_SCALE}, and \texttt{MOVEMENT\_SCALE}; and at the top of
 \path{Assets/Scripts/TowerDefence/Level/GenomeManager.cs}, with
-\texttt{POPULATION_SIZE}, \texttt{MUTATION_RATE}, \texttt{GROWTH_RATE},
-\texttt{SPAWN_DELAY}, and \texttt{STARTING_TOTAL}. The scale constants in
+\texttt{POPULATION\_SIZE}, \texttt{MUTATION\_RATE}, \texttt{GROWTH\_RATE},
+\texttt{SPAWN\_DELAY}, and \texttt{STARTING\_TOTAL}. The scale constants in
 \path{Genome.cs} change how health, speed, and damage are scaled relative to
-each other. \texttt{POPULATION_SIZE} represents the number of genomes (and
-therefore zombunnies) in every generation. \texttt{MUTATION_RATE} determines how
-much variance there is in everey mutation operation. \texttt{GROWTH_RATE}
+each other. \texttt{POPULATION\_SIZE} represents the number of genomes (and
+therefore zombunnies) in every generation. \texttt{MUTATION\_RATE} determines how
+much variance there is in every mutation operation. \texttt{GROWTH\_RATE}
 Determines how much combined speed, health, and damage is available to be
-distributed. \texttt{SPAWN_DELAY} determines how much time passes between spawns
-in waves. \texttt{STARTING_TOTAL} determines the total number of stats available
+distributed. \texttt{SPAWN\_DELAY} determines how much time passes between spawns
+in waves. \texttt{STARTING\_TOTAL} determines the total number of stats available
 to the zombunnies at the start of the game.

### 2018-12-12 TD/TowerDefense/Assets/Scripts/ActionGameFramework/Projectiles/BallisticProjectile.cs

@@ -112,7 +112,14 @@ namespace ActionGameFramework.Projectiles
 					}
 					foreach (Collider projectileCollider in m_Colliders)
 					{
-						Physics.IgnoreCollision(colliderToIgnore, projectileCollider, true);
+                        try
+                        {
+                            Physics.IgnoreCollision(colliderToIgnore, projectileCollider, true);
+                        } catch
+                        {
+                            //TODO: FIXME
+                        }
+						
 					}
 					m_CollidersIgnoring.Add(colliderToIgnore);
 				}

### 2018-12-12 TD/TowerDefense/Assets/Scripts/Evolution/Genome.cs

@@ -10,7 +10,7 @@ namespace Evolution
 {
     public class Genome
     {
-        private readonly static float HEALTH_SCALE = 1;
+        private readonly static float HEALTH_SCALE = 0.3f;
         private readonly static float DAMAGE_SCALE = 1;
         private readonly static float MOVEMENT_SCALE = 0.4f;
 
@@ -67,7 +67,7 @@ namespace Evolution
                 speed_scalar = (float)stat_array[0];
                 damage_scalar = (float)stat_array[1];
                 health_scalar = (float)stat_array[2];
-                MonoBehaviour.print($"Health: ({health_scalar}, {Health}), Damage: ({damage_scalar}, {Damage}), Speed: ({speed_scalar}, {MovementSpeed})");
+                //MonoBehaviour.print($"Health: ({health_scalar}, {Health}), Damage: ({damage_scalar}, {Damage}), Speed: ({speed_scalar}, {MovementSpeed})");
             }
         }
 

### 2018-12-12 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAgent.cs

@@ -18,6 +18,8 @@ namespace TowerDefense.Agents
         private readonly static float SINK_SPEED = 2.5f;
         private readonly static float SINK_TIME = 2.0f;
         private readonly static float STARVATION_DISTANCE = 40.0f;
+        private readonly static double DISTANCE_FITNESS_SCALE = 3.0;
+        private readonly static double DAMAGE_FITNESS_SCALE = 1.0;
 
         public override Vector3 velocity
         {
@@ -26,8 +28,12 @@ namespace TowerDefense.Agents
         }
         private PolarVector lastVelocity;
 
+        private double fitness;
         public double Fitness {
-            get { return this.damageDone; }
+            get
+            {
+                return this.fitness;
+            }
         }
 
         // Set of nearby objects
@@ -50,7 +56,7 @@ namespace TowerDefense.Agents
         // Increment total damage done over a zombie's lifetime
         public void addDamageDone(float increment)
         {
-            this.damageDone += increment;
+            fitness += increment * DAMAGE_FITNESS_SCALE;
         }
 
         // Get alignment of zombie with this.configuration.alignment
@@ -92,7 +98,7 @@ namespace TowerDefense.Agents
             target.y = 0;
             spawnPostition.y = 0;
             var difference = target - spawnPostition;
-            print($"Target: {target}, Spawn: {spawnPostition}, Difference: {difference}");
+            //print($"Target: {target}, Spawn: {spawnPostition}, Difference: {difference}");
             lastVelocity = PolarVector.fromVector3(difference);
             this.genome = genome;
             var health = genome.Health;
@@ -188,6 +194,8 @@ namespace TowerDefense.Agents
             rigidBody.isKinematic = true;
             damageCollider.isTrigger = false;
             anim.SetTrigger("Dead");
+            //Fixme, currently does position from origin instead of home base.
+            fitness += transform.position.magnitude * DISTANCE_FITNESS_SCALE;
         }
     }
 }

### 2018-12-12 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAttacker.cs

@@ -20,7 +20,8 @@ public class ZombieAttacker : MonoBehaviour {
 
     private void OnTriggerEnter(Collider other)
     {
-        toAttack.Add(other.gameObject.GetComponent<Targetable>());
+        if (other != null && other.gameObject != null && other.gameObject.GetComponent<Targetable>() != null)
+            toAttack.Add(other.gameObject.GetComponent<Targetable>());
     }
 
     private void OnTriggerExit(Collider other)

### 2018-12-12 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/GenomeManager.cs

@@ -13,20 +13,20 @@ namespace TowerDefense.Level
         /// <summary>
         /// How many zombunnies to spawn
         /// </summary>
-        public static readonly int POPULATION_SIZE = 500;
+        public static readonly int POPULATION_SIZE = 200;
 
         /// <summary>
         /// The mutation rate
         /// </summary>
-        public static readonly float MUTATION_RATE = 0.2f;
+        public static readonly float MUTATION_RATE = 0.5f;
 
-        public static readonly float GROWTH_RATE = 0.3f;
+        public static readonly float GROWTH_RATE = 0.0f;
 
-        public static readonly float SPAWN_DELAY = .2f;
+        public static readonly float SPAWN_DELAY = .1f;
 
         private static readonly float STARTING_TOTAL = 16f;
 
-        private static readonly double INITIAL_FITNESS = 0.0;
+        private static readonly double INITIAL_FITNESS = 1.0;
 
         /// <summary>
         /// The prefab to spawn as an enemy
@@ -69,26 +69,36 @@ namespace TowerDefense.Level
             {
                 currentMap.Add(Genome.RandomGenome(sampler, STARTING_TOTAL), INITIAL_FITNESS);
             }
-            print(currentMap.Count);
             prefabAgent = ZombiePrefab.GetComponent<ZombieAgent>();
         }
 
         private void NextWave()
         {
-            var nextWave = new Stack<Genome>(POPULATION_SIZE);
-
             //Cull wave
             var culled = Cull(currentMap);
-            
-            // Reproduce Here! dict -> list
-            
 
-            foreach (var pair in currentMap)
+            //Reproduce and scramble order
+            var reproduced = Reproduce(culled);
+
+            // Mutate
+            var nextWave = mutate(reproduced);
+            print($"{currentMap.Count} {culled.Count} {reproduced.Count}");
+
+            //Calculate averages
+            float avg_speed = 0;
+            float avg_damage = 0;
+            float avg_health = 0;
+            foreach (var genome in nextWave)
             {
-                if (pair.Key == null) continue;
-                nextWave.Push(pair.Key.mutate(sampler, GROWTH_RATE));
+                avg_speed += genome.MovementSpeed;
+                avg_health += genome.Health;
+                avg_damage += genome.Damage;
             }
-            // Scramble list here
+            avg_speed /= POPULATION_SIZE;
+            avg_health /= POPULATION_SIZE;
+            avg_damage /= POPULATION_SIZE;
+
[…]

### 2018-12-12 paper.tex
Paper: fix Zombunny capitialization

@@
 each other. \texttt{POPULATION\_SIZE} represents the number of genomes (and
-therefore zombunnies) in every generation. \texttt{MUTATION\_RATE} determines how
+therefore Zombunnies) in every generation. \texttt{MUTATION\_RATE} determines how
 much variance there is in every mutation operation. \texttt{GROWTH\_RATE}
@@
 in waves. \texttt{STARTING\_TOTAL} determines the total number of stats available
-to the zombunnies at the start of the game.
+to the Zombunnies at the start of the game.
 

### 2018-12-12 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAgent.cs
Selection distribution improvements

@@ -195,7 +195,7 @@ namespace TowerDefense.Agents
             damageCollider.isTrigger = false;
             anim.SetTrigger("Dead");
             //Fixme, currently does position from origin instead of home base.
-            fitness += transform.position.magnitude * DISTANCE_FITNESS_SCALE;
+            fitness -= transform.position.magnitude * DISTANCE_FITNESS_SCALE;
         }
     }
 }

### 2018-12-12 TD/TowerDefense/Assets/Scripts/TowerDefense/Agents/ZombieAttacker.cs

@@ -21,13 +21,20 @@ public class ZombieAttacker : MonoBehaviour {
     private void OnTriggerEnter(Collider other)
     {
         if (other != null && other.gameObject != null && other.gameObject.GetComponent<Targetable>() != null)
-            toAttack.Add(other.gameObject.GetComponent<Targetable>());
+            try
+            {
+                toAttack.Add(other.gameObject.GetComponent<Targetable>());
+            }
+            catch { }
     }
 
     private void OnTriggerExit(Collider other)
     {
-        Targetable leavingTargetable = other.gameObject.GetComponent<Targetable>();
-        toAttack.Remove(leavingTargetable);
+        if (other != null && other.gameObject != null && other.gameObject.GetComponent<Targetable>() != null)
+        {
+            Targetable leavingTargetable = other.gameObject.GetComponent<Targetable>();
+            toAttack.Remove(leavingTargetable);
+        }
     }
 
     private void Update()

### 2018-12-12 TD/TowerDefense/Assets/Scripts/TowerDefense/Level/GenomeManager.cs

@@ -28,6 +28,9 @@ namespace TowerDefense.Level
 
         private static readonly double INITIAL_FITNESS = 1.0;
 
+        // Must be greater than 1
+        private static readonly double CHANCE_BASE = 5;
+
         /// <summary>
         /// The prefab to spawn as an enemy
         /// </summary>
@@ -141,7 +144,8 @@ namespace TowerDefense.Level
 
         private static List<Pair<double, Genome>> Cull(Dictionary<Genome, double> toCull)
         {
-            double max_fitness = 0;
+            double max_fitness = toCull.GetEnumerator().Current.Value;
+            double min_fitness = toCull.GetEnumerator().Current.Value;
             foreach (var fitness in toCull.Values)
             {
                 if (fitness > max_fitness)
@@ -151,9 +155,22 @@ namespace TowerDefense.Level
             }
 
             var ret = new List<Pair<double, Genome>>(toCull.Count);
+
+            //Handle divide by 0 case
+            if (max_fitness == min_fitness)
+            {
+                foreach(var pair in toCull)
+                {
+                    ret.Add(new Pair<double, Genome>(pair.Value, pair.Key));
+                }
+                return ret;
+            }
+
+            
             foreach (var pair in toCull)
             {
-                var chance = pair.Value / max_fitness;
+                var squashed = (pair.Value - min_fitness) / (max_fitness - min_fitness);
+                var chance = System.Math.Pow(squashed, 1/CHANCE_BASE);
                 if (Random.value < chance || pair.Value == max_fitness)
                 {
                     ret.Add(new Pair<double, Genome>(pair.Value, pair.Key));

### 2018-12-12 paper.tex
Paper: add genetic alg section

@@
 
-In \tavs,
+In \tavs, evolution is done in three steps: culling, reproduction, and mutation.
+To cull the genomes with low fitness, the entire range of genome values is
+compressed down on to the values from zero to one, and then fed through a square
+root function. The result is the probability that the given genome survives to
+the next wave. The square root function has the nice properties that it passes
+through \((1,1)\), so at least one genome will always survive, it passes through
+\((0,0)\), so at least one genome will die, and other values are scaled
+non-linearly such that only the really unfit genomes have a high probability of
+dying.
+
+The surviving genomes are then passed to the reproduction function, which
+selects a weighted random genome to duplicate and add to the next wave until
+the total is back up to the set population count. The randomness is weighted
+linearly; all of the genome fitnesses are summed, and then a random number is
+picked between 0 and this sum, effectively creating a ``bucket'' the size of the
+each fitness for the random number to choose between.
+
+The mutation phase takes the result of reproduction and adds a
+Gaussian-distributed random value to each characteristic of the Genome. The
+results are then passed to the game portion to be spawned as another wave of
+Zombunnies.
 

### 2018-12-12 paper.tex
Paper: genome and polarvector

@@
 \subsubsection{PolarVector}
-The PolarVector class encapsulates the internal representation that we use for storing and passing vectors to the neural net, as well as keeping track of the previous direction a Zombunny was headed during the previous tick.
-The PolarVector class essentially wraps a float, direction (in degrees) and a float, magnitude, which provides sufficient information to create a new vector in two-dimensional space.
-The PolarVector class provides some convenient helper methods for converting between Cartesian and Polar coordinate systems, as the Unity engine primarily uses Cartesian coordinates.
+The PolarVector class encapsulates the internal representation that we use for
+storing and passing vectors to the neural net, as well as keeping track of the
+previous direction a Zombunny was headed during the previous tick. The
+PolarVector class essentially wraps a float, direction (in degrees) and a float,
+magnitude, which provides sufficient information to create a new vector in
+two-dimensional space. The PolarVector class provides some convenient helper
+methods for converting between Cartesian and Polar coordinate systems, as the
+Unity engine primarily uses Cartesian coordinates.
 
@@
 health, movement speed, and damage, which need to be set manually as discussed
-in the hyperparameters sections. The Id field is used as a unique identifier if
+in the hyperparameters sections. The \texttt{Id} field is used as a unique identifier if
 genomes need to be looked up, and also ensures that every genome will hash differently.
@@
 
-The mutation function in Figure 8 essentially creates a new copy of the current genome, which is then nudged by normally distributed random numbers.
+The \texttt{mutation} function in Figure 8 essentially creates a new copy of the current genome, which is then nudged by normally distributed random numbers.
 

### 2018-12-12 paper.tex
Paper: ALL THE TEXTTT

@@
 
-The GenomeManager class keeps track of game-wide genome management, i.e.
-selection and reproduction, as well as spawning Zombunnies and initiating new waves.
-The GenomeManager holds onto a collection of all genomes in a wave-by-wave list of hashmaps that map genomes to their fitness.
-The primary properties of the GenomeManager class can be seen in Figure 9, with various hardcoded constants that can be adjusted to influence general properties of the evolution, as well as the genomeMaps object, which contains the aforementioned collection of all genomes used in the course of evolution thus far.
+The \texttt{GenomeManager} class keeps track of game-wide state and genome tasks, i.e.
+selection and reproduction, as well as spawning Zombunnies and initiating new
+waves. The \texttt{GenomeManager} holds onto a collection of all genomes in a
+wave-by-wave list of hashmaps that map genomes to their fitness. The primary
+properties of the \texttt{GenomeManager} class can be seen in Figure 9, with various
+hardcoded constants that can be adjusted to influence general properties of the
+evolution, as well as the genomeMaps object, which contains the aforementioned
+collection of all genomes used in the course of evolution thus far.
 
@@
 
-The initialization process of GenomeManager (see Figure 10) consists primarily of allocating the containing data structures for the various stages of the genome life cycle, followed by creating a first wave with randomized genomes and zero fitness.
-It should also be noted that we initialize our ZigguratGaussianSampler here from the Redzen library, which provides a fast way of generating normally-distributed floating-point numbers.
+The initialization process of \texttt{GenomeManager} (see Figure 10) consists primarily of allocating the containing data structures for the various stages of the genome life cycle, followed by creating a first wave with randomized genomes and zero fitness.
+It should also be noted that we initialize our \texttt{ZigguratGaussianSampler} here from the Redzen library, which provides a fast way of generating normally-distributed floating-point numbers.
 
@@
 
-The Spawn method, as seen in Figure 12, is called at every SPAWN\_DELAY interval POPULATION\_COUNT times.
-The function starts by spawning a Zombunny with no genome due to the inability to provide parameters upon GameObject instantiation.
-Therefore, we set the genome after the fact, popping it off of the toSpawn stack, also adding the ZombieDied function to the removed event on said Zombunny, which allows us to execute code in the context of the GenomeManager upon Zombunny death; namely, ZombunnyDied.
-ZombunnyDied handles finding the fitness of Zombunnies and adding them to the list of completed genomes, as well as calling NextWave again when the last Zombunny in the wave dies.
+The \texttt{Spawn} method, as seen in Figure 12, is called at every
+\texttt{SPAWN\_DELAY} interval \texttt{POPULATION\_COUNT} times. The function
+starts by spawning a Zombunny with no genome due to the inability to provide
+parameters upon GameObject instantiation. Therefore, we set the genome after the
+fact, popping it off of the \texttt{toSpawn} stack, also adding the \texttt{ZombieDied} function
+to the removed event on said Zombunny, which allows us to execute code in the
+context of the \texttt{GenomeManager} upon Zombunny death; namely, \texttt{ZombunnyDied}.
+ZombunnyDied handles finding the fitness of Zombunnies and adding them to the
+list of completed genomes, as well as calling \texttt{NextWave} again when the last
+Zombunny in the wave dies.
 
@@
 
-ZombieAgent is a GameObject which determines Zombunny behavior and stats from a genome and keeps track of fitness for each individual Zombunny.
-To do so, ZombieAgent pulls all the stat-determining values from the genome and applies them upon instantiation, i.e.
-setting health, damage, and speed as determined by the genome, as well as handling tick-to-tick operations during a Zombunny's lifetime.
-These tick-to-tick operations include choosing the next movement vector based on the location of nearby GameObjects and agents' current status.
+\texttt{ZombieAgent} is a \texttt{GameObject} which determines Zombunny behavior
+and stats from a genome and keeps track of fitness for each individual Zombunny.
+To do so, \texttt{ZombieAgent} pulls all the stat-determining values from the
+genome and applies them upon instantiation, i.e. setting health, damage, and
+speed as determined by the genome, as well as handling tick-to-tick operations
+during a Zombunny's lifetime. These tick-to-tick operations include choosing the
+next movement vector based on the location of nearby \texttt{Targetables} and agents' current status.
 
@@
 
-In Figure 13, observe that the ZombieAgent class inherits from the Targetable class.
-Targetable is the parent class for every GameObject in the Action Game Framework, which can be automatically fired upon by ranged weapons, i.e.
-targeted.
-This also allows any existing defenses from the default game or any other targeting GameObject from the Action Game Framework to work without extra compatibility code.
-SINK\_SPEED and SINK\_TIME are constants used for death animation.
-velocity provides the Zombunny's current velocity for any consumers of the Targetable parent class.
-LastVelocity stores the previous movement vector as a PolarVector, in a format more congenial to the pathfinding algorithm.
-Fitness is an interface used to grab the effectiveness of this ZombieAgent at the end of its lifespan by the GenomeManager class.
-inVision keeps track of all nearby objects that the Zombunny can see for use in its pathfinding algorithm.
-the alignment is used for purposes of checking whether a Zombunny can damage other GameObjects, while visionCollider and damageCollider are the areas within which a Zombunny can see and deal damage from, respectively.
-The Rigidbody rigidBody handles physical collisions for movement purposes, while anim keeps track of the Zombunny's animation state, namely walking, idling, or death.
+In Figure 13, observe that the \texttt{ZombieAgent} class inherits from the
+\texttt{Targetable} class. \texttt{Targetable} is the parent class for every
+GameObject in the Action Game Framework that can be automatically
+fired upon by ranged weapons, i.e. targeted. This also allows any existing
+defenses from the default game or any other targeting GameObject from the Action
+Game Framework to work without extra compatibility code. \texttt{SINK\_SPEED} and
+\texttt{SINK\_TIME} are constants used for death animation. \texttt{velocity} provides the
+Zombunny's current velocity for any consumers of the \texttt{Targetable} parent class.
+\texttt{LastVelocity} stores the previous movement vector as a \texttt{PolarVector}, in a format
+more congenial to the pathfinding algorithm. \texttt{Fitness} is an interface used to
+grab the effectiveness of this \texttt{ZombieAgent} at the end of its lifespan by the
+\texttt{GenomeManager} class. \texttt{inVision} keeps track of all nearby objects that the
+Zombunny can see for use in its pathfinding algorithm. \texttt{alignment} is used for
+purposes of checking whether a Zombunny can damage other \texttt{Targetables}, while
+\texttt{visionCollider} and \texttt{damageCollider} are the areas within which a Zombunny can see
+and deal damage from, respectively. The Rigidbody \texttt{rigidBody} handles physical
+collisions for movement purposes, while \texttt{anim} keeps track of the Zombunny's
+animation state, namely walking, idling, or death.
 
@@
 
-In Figure 14, one can see the Genome, Awake, and Start methods of the
-ZombieAgent class. Genome instantiates a Zombunny's Genome object by pulling the
-var health from the given Genome, calling the SetMaxHealth and SetHealth
+In Figure 14, one can see the \texttt{Genome}, \texttt{Awake}, and \texttt{Start} methods of the
+\texttt{ZombieAgent} class. \texttt{Genome} instantiates a Zombunny's Genome object by pulling the
+health from the given \texttt{Genome,} calling the \texttt{SetMaxHealth} and \texttt{SetHealth}
 methods, and setting the initial velocity vector to have an initial direction of
 $270^\circ$\----that is, in the general direction of the player's base relative
-to the spawn location, and magnitude determined by the MovementSpeed variable
-from the given Genome. Awake calls the underlying (base) Awake function and adds
-custom OnDeath behavior to a Zombunny. Start initializes the inVision HashSet of
-Targetable objects, which keeps track of nearby visible GameObjects. In the
-unexpected case that genome or lastVelocity are null, Start initializes these to
+to the spawn location, and magnitude determined by the \texttt{MovementSpeed} variable
+from the given \texttt{Genome}. \texttt{Awake} calls the underlying (base) \texttt{Awake} function and adds
+custom \texttt{OnDeath} behavior to a Zombunny. \texttt{Start} initializes the \texttt{inVision} \texttt{HashSet} of
+\texttt{Targetable} objects, which keeps track of nearby visible \texttt{GameObjects}. In the
+unexpected (this is a concurrency issue) case that \texttt{genome} or \texttt{lastVelocity} are \texttt{null}, \texttt{Start} initializes these to
 default values (the "Zero" genome and a default velocity vector).
 
-\imfigH{ZombieAgentVision}{Methods for keeping track of GameObjects entering
-  and exiting a Zombunny's visionCollider}
+\imfigH{ZombieAgentVision}{Methods for keeping track of \texttt{GameObjects} entering
+  and exiting a Zombunny's \texttt{visionCollider}}
 
-Figure 15 shows the OnTriggerEnter and OnTriggerExit methods of the ZombieAgent
-class, which are used in conjunction with a Zombunny's visionCollider to update
-the inVision HashSet whenever a GameObject enters or exits the Zombunny's
-visionCollider radius.
+Figure 15 shows the \texttt{OnTriggerEnter} and \texttt{OnTriggerExit} methods of the \texttt{ZombieAgent}
+class, which are used in conjunction with a Zombunny's \texttt{visionCollider} to update
+the \texttt{inVision} \texttt{HashSet} whenever a \texttt{GameObject} enters or exits the Zombunny's
+\texttt{visionCollider} radius.
 
-\imfigH{ZombieAgentUpdateNearby}{The portion of the FixedUpdate method for
+\imfigH{ZombieAgentUpdateNearby}{The portion of the \texttt{FixedUpdate} method for
 determining the position of nearby objects relative to a Zombunny}
@@
 Figure 16 shows the functions used to determine the position of GameObjects in
-inVision relative to a Zombunny's previous direction vector, stored as a
+\texttt{inVision} relative to a Zombunny's previous direction vector, stored as a
 dictionary of Targetables to PolarVectors. This allows a Zombunny to keep track
@@
 
-\imfig{ZombieAgentUpdateMovement}{The function of FixedUpdate that handles
+\imfig{ZombieAgentUpdateMovement}{The function of \texttt{FixedUpdate} that handles
   movement between ticks}
 
-Figure 17 shows the portion of FixedUpdate dedicated to altering a Zombunny's
-trajectory from tick to tick, calling the Rotate method of the lastVelocity
-PolarVector using the CalculateDirection method of the genome class, taking into
+Figure 17 shows the portion of \texttt{FixedUpdate} dedicated to altering a Zombunny's
+trajectory from tick to tick, calling the \texttt{Rotate} method of the \texttt{lastVelocity}
+\texttt{PolarVector} using the \texttt{CalculateDirection} method of the genome class, taking into
 account the Zombunny's previous velocity vector, time alive, current health, and
@@
 
-\imfig{ZombieAgentUpdateDeath}{The portion of FixedUpdate that handles
+\imfig{ZombieAgentUpdateDeath}{The portion of \texttt{FixedUpdate} that handles
   death/deletion}
 
-Figure 18 shows the part of the FixedUpdate method which keeps track of Zombunny
+Figure 18 shows the part of the \texttt{FixedUpdate} method which keeps track of Zombunny
 death, destroying the Zombunny GameObject at the appropriate time and calling
 the relevant death animations. For every tick that a Zombunny is not dead,
-FixedUpdate increments timeAlive, which is later used as a factor in
+\texttt{FixedUpdate} increments \texttt{timeAlive}, which is later used as a factor in
 calculating fitness.
@@
 
-The ZombieAttacker class (see Figure 19) calls Update on each tick, dealing damage to any item
-in toAttack, which is a HashSet of Targetable GameObjects that intersect with
+The \texttt{ZombieAttacker} class (see Figure 19) calls \texttt{Update} on each tick, dealing damage to any item
+in \texttt{toAttack}, which is a \texttt{HashSet} of \texttt{Targetable} GameObjects that intersect with
 a Zombunny's attack collider (see Figure 4). This way, a Zombunny can attack
-multiple GameObjects so long as they intersect with its attack collider. Damage
-is applied to items in toAttack by calling their individual takeDamage methods.
-Damage dealt is determined by the Zombunny's genome, and is passed as a parameter
-to takeDamage.
+multiple GameObjects so long as they intersect with its (tiny) attack collider.
+Ideally the Zombunny would only attack one other entitiy at a time, however
+attempting to do so results in a lot of edge cases and extra computational work,
+so we opted to attack everything in range. Damage
+is applied to items in \texttt{toAttack} by calling their individual
+\texttt{takeDamage} methods. The amount of damage dealt is determined by the Zombunny's genome, and is passed as a parameter
+to \texttt{takeDamage}.
 
-\imfig{ZombieAttacker}{The Update method of the ZombieAttacker class}
+\imfig{ZombieAttacker}{The \texttt{Update} method of the \texttt{ZombieAttacker} class}
 
